---
title: "Financial Aid Distributions"
author: "Peter Granville"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    toc: true
    toc_float: true
  
---

```{r setDefault, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r axisTitles, include=FALSE}

axisTitles1 <- data.frame(
  `Target name` = character(), 
  `Measure name` = character(), 
  `Title name` = character(), 
  check.names=FALSE
) 

axisTitles1 <- axisTitles1 %>% add_row(
  `Target name`="Tuition and fees paid",  `Measure name`="Median", `Title name`="Median tuition and fees"
) %>% add_row(
  `Target name`="Tuition and fees minus all grants",  `Measure name`="Share >0", `Title name`="Share with unmet tuition and fees after all grants"
) %>% add_row(
  `Target name`="Tuition and fees minus all grants",  `Measure name`="Median", `Title name`="Median net tuition and fees after all grants"
) %>% add_row(
  `Target name`="Tuition and fees minus all grants",  `Measure name`="Average", `Title name`="Average net tuition and fees after all grants"
) %>% add_row(
  `Target name`="Total state and institutional grants",  `Measure name`="Share >0", `Title name`="Share receiving state or institutional grants"
) %>% add_row(
  `Target name`="Total state and institutional grants",  `Measure name`="Average", `Title name`=" Average combined state and institutional grant award"
) %>% add_row(
  `Target name`="Title IV loans (includes Parent PLUS Loans)",  `Measure name`="Share >0", `Title name`="Share receiving Title IV loans (includes Parent PLUS Loans)"
) %>% add_row(
  `Target name`="Title IV loans (includes Parent PLUS Loans)",  `Measure name`="Average", `Title name`="Average Title IV loan amount (includes Parent PLUS Loans)"
) %>% add_row(
  `Target name`="Student budget minus all grants",  `Measure name`="Median", `Title name`="Median net student budget after all grants"
) %>% add_row(
  `Target name`="Student budget minus all grants",  `Measure name`="Average", `Title name`="Average net student budget after all grants"
) %>% add_row(
  `Target name`="Student budget (attendance adjusted)",  `Measure name`="Median", `Title name`="Median student budget (attendance adjusted)"
) %>% add_row(
  `Target name`="State non-need & merit grants",  `Measure name`="Share >0", `Title name`="Share receiving state non-need & merit grants"
) %>% add_row(
  `Target name`="State non-need & merit grants",  `Measure name`="Average", `Title name`="Average state non-need & merit grant award"
) %>% add_row(
  `Target name`="State need-based grants",  `Measure name`="Share >0", `Title name`="Share receiving state need-based grants"
) %>% add_row(
  `Target name`="State need-based grants",  `Measure name`="Average", `Title name`="Average state need-based grant award"
) %>% add_row(
  `Target name`="State grants total",  `Measure name`="Share >0", `Title name`="Share receiving state grants"
) %>% add_row(
  `Target name`="State grants total",  `Measure name`="Average", `Title name`="Average state grant award"
) %>% add_row(
  `Target name`="Private source grants",  `Measure name`="Share >0", `Title name`="Share receiving private source grants"
) %>% add_row(
  `Target name`="Private source grants",  `Measure name`="Average", `Title name`="Average private source grant award"
) %>% add_row(
  `Target name`="Net tuition after all grants as percent of income",  `Measure name`="Median", `Title name`="Median net tuition after all grants as percent of income"
) %>% add_row(
  `Target name`="Net price after grants as percent of income",  `Measure name`="Median", `Title name`="Median net price after grants as percent of income"
) %>% add_row(
  `Target name`="Institutional need-based grants",  `Measure name`="Share >0", `Title name`="Share receiving institutional need-based grants"
) %>% add_row(
  `Target name`="Institutional need-based grants",  `Measure name`="Average", `Title name`="Average institutional need-based grant award"
) %>% add_row(
  `Target name`="Institution non-need & merit grants",  `Measure name`="Share >0", `Title name`="Share receiving institutional non-need & merit grants"
) %>% add_row(
  `Target name`="Institution non-need & merit grants",  `Measure name`="Average", `Title name`="Average institutional non-need & merit grant award"
) %>% add_row(
  `Target name`="Institution grants total",  `Measure name`="Share >0", `Title name`="Share receiving institutional grants"
) %>% add_row(
  `Target name`="Institution grants total",  `Measure name`="Average", `Title name`="Average institutional grant award"
) %>% add_row(
  `Target name`="Grant amount exceeding federal need",  `Measure name`="Share >0", `Title name`="Share whose grants exceed federal need"
) %>% add_row(
  `Target name`="Grant amount exceeding federal need",  `Measure name`="Average", `Title name`="Average grant amount in excess of federal need"
) %>% add_row(
  `Target name`="Federal Pell Grant",  `Measure name`="Share >0", `Title name`="Share receiving federal Pell Grants"
) %>% add_row(
  `Target name`="Federal Pell Grant",  `Measure name`="Average", `Title name`="Average federal Pell Grant award"
) %>% add_row(
  `Target name`="Federal campus-based aid (SEOG, FWS)",  `Measure name`="Share >0", `Title name`="Share receiving federal campus-based aid (SEOG, FWS)"
) %>% add_row(
  `Target name`="Federal campus-based aid (SEOG, FWS)",  `Measure name`="Average", `Title name`="Average federal campus-based aid award (SEOG, FWS)"
) %>% add_row(
  `Target name`="Expected Family Contribution",  `Measure name`="Median", `Title name`="Median Expected Family Contribution"
)

```

```{r setBounds, include=FALSE}

suppressWarnings({
  
  AMP.SECTOR3 <- AMP.SECTOR3 %>% separate(
    `Target confidence interval`, c("Lower bound", "Upper bound"), " - "
  ) %>% mutate(
    `Target value` = gsub(" !!", "", `Target value`), 
    `Target value` = gsub(" !", "", `Target value`), 
    `Target value` = gsub(",", "", `Target value`), 
    `Lower bound` = gsub(" !!", "", `Lower bound`), 
    `Lower bound` = gsub(" !", "", `Lower bound`), 
    `Lower bound` = gsub(",", "", `Lower bound`), 
    `Upper bound` = gsub(" !!", "", `Upper bound`), 
    `Upper bound` = gsub(" !", "", `Upper bound`),
    `Upper bound` = gsub(",", "", `Upper bound`)
  ) %>% mutate(
    `Target value` = as.numeric(`Target value`), 
    `Lower bound` = as.numeric(`Lower bound`), 
    `Upper bound` = as.numeric(`Upper bound`)
  )
  
  AMP.INSTSTAT.2Y <- AMP.INSTSTAT.2Y %>% separate(
    `Target confidence interval`, c("Lower bound", "Upper bound"), " - "
  ) %>% mutate(
    `Target value` = gsub(" !!", "", `Target value`), 
    `Target value` = gsub(" !", "", `Target value`), 
    `Target value` = gsub(",", "", `Target value`), 
    `Lower bound` = gsub(" !!", "", `Lower bound`), 
    `Lower bound` = gsub(" !", "", `Lower bound`), 
    `Lower bound` = gsub(",", "", `Lower bound`), 
    `Upper bound` = gsub(" !!", "", `Upper bound`), 
    `Upper bound` = gsub(" !", "", `Upper bound`),
    `Upper bound` = gsub(",", "", `Upper bound`)
  ) %>% mutate(
    `Target value` = as.numeric(`Target value`), 
    `Lower bound` = as.numeric(`Lower bound`), 
    `Upper bound` = as.numeric(`Upper bound`)
  )
  
  AMP.INSTSTAT.4Y <- AMP.INSTSTAT.4Y %>% separate(
    `Target confidence interval`, c("Lower bound", "Upper bound"), " - "
  ) %>% mutate(
    `Target value` = gsub(" !!", "", `Target value`), 
    `Target value` = gsub(" !", "", `Target value`), 
    `Target value` = gsub(",", "", `Target value`), 
    `Lower bound` = gsub(" !!", "", `Lower bound`), 
    `Lower bound` = gsub(" !", "", `Lower bound`), 
    `Lower bound` = gsub(",", "", `Lower bound`), 
    `Upper bound` = gsub(" !!", "", `Upper bound`), 
    `Upper bound` = gsub(" !", "", `Upper bound`),
    `Upper bound` = gsub(",", "", `Upper bound`)
  ) %>% mutate(
    `Target value` = as.numeric(`Target value`), 
    `Lower bound` = as.numeric(`Lower bound`), 
    `Upper bound` = as.numeric(`Upper bound`)
  )
  
  DIST.SECTOR3 <- DIST.SECTOR3 %>% separate(
    `Interval`, c("Lower bound", "Upper bound"), " - "
  ) %>% mutate(
    `Share` = gsub(" !!", "", `Share`), 
    `Share` = gsub(" !", "", `Share`), 
    `Share` = gsub(",", "", `Share`), 
    `Lower bound` = gsub(" !!", "", `Lower bound`), 
    `Lower bound` = gsub(" !", "", `Lower bound`), 
    `Lower bound` = gsub(",", "", `Lower bound`), 
    `Upper bound` = gsub(" !!", "", `Upper bound`), 
    `Upper bound` = gsub(" !", "", `Upper bound`),
    `Upper bound` = gsub(",", "", `Upper bound`)
  ) %>% mutate(
    `Share` = as.numeric(`Share`), 
    `Lower bound` = as.numeric(`Lower bound`), 
    `Upper bound` = as.numeric(`Upper bound`)
  )
    
})

minValues <- rbind(
  aggregate(data=AMP.SECTOR3, `Lower bound` ~ `Target name` + `Measure name`, FUN=min), 
  aggregate(data=AMP.INSTSTAT.2Y, `Lower bound` ~ `Target name` + `Measure name`, FUN=min), 
  aggregate(data=AMP.INSTSTAT.4Y, `Lower bound` ~ `Target name` + `Measure name`, FUN=min)
) %>% filter(`Measure name` %in% c("Median", "Average"))

maxValues <- rbind(
  aggregate(data=AMP.SECTOR3, `Upper bound` ~ `Target name` + `Measure name`, FUN=max), 
  aggregate(data=AMP.INSTSTAT.2Y, `Upper bound` ~ `Target name` + `Measure name`, FUN=max), 
  aggregate(data=AMP.INSTSTAT.4Y, `Upper bound` ~ `Target name` + `Measure name`, FUN=max)
) %>% filter(`Measure name` %in% c("Median", "Average"))

minValues <- aggregate(data=minValues, `Lower bound` ~ `Target name`, FUN=min)
maxValues <- aggregate(data=maxValues, `Upper bound` ~ `Target name`, FUN=max)

axisBounds <- full_join(
  x=minValues, y=maxValues, by="Target name"
) %>% rename(
  `Lower bound for axis` = `Lower bound`, 
  `Upper bound for axis` = `Upper bound`
) %>% mutate(
  `Distance between bounds` = `Upper bound for axis` - `Lower bound for axis`
) %>% mutate(
  `Extra margin` = `Distance between bounds` * 0.03
) %>% mutate(
  `Lower bound for axis` = `Lower bound for axis` - `Extra margin`, 
  `Upper bound for axis` = `Upper bound for axis` + `Extra margin`
) %>% select(
  -(`Distance between bounds`), -(`Extra margin`)
)

rm(minValues, maxValues)

```

```{r chartFn1, include=FALSE}

chartFn1 <- function(targetName, rowName, measureName, subtable, sector3Val){
  
  # targetName <- "Federal Pell Grant"
  # rowName <- "Income Quartile"
  # measureName <- "Share >0"
  # subtable <- "SECTOR3"
  # sector3Val <- "None"

  if(subtable=="SECTOR3"){
    tempDF <- AMP.SECTOR3
  }else{
    if(subtable=="INSTSTAT"){
      if(sector3Val=="Public 4-year"){
        tempDF <- AMP.INSTSTAT.4Y
      }else{
        if(sector3Val=="Public 2-year"){
          tempDF <- AMP.INSTSTAT.2Y
        }else{
          stop("Bad sector3Val input")
        }
      }
    }else{
      stop("Bad subtable input")
    }
  }
  
  tempDF <- tempDF %>% filter(
    `Target name`==targetName, 
    `Row name`==rowName, 
    `Measure name`==measureName
  )
  tempDF <- left_join(x=tempDF, y=axisTitles1, by=c("Target name", "Measure name"))
  tempDF <- left_join(x=tempDF, y=axisBounds, by="Target name")
  
  if(measureName=="Share >0"){
    tempDF <- tempDF %>% mutate(
      `Target value` = `Target value` / 100, 
      `Lower bound` = `Lower bound` / 100, 
      `Upper bound` = `Upper bound` / 100
    ) %>% mutate(
      `Target value` = ifelse(`Target value` < 0, 0, `Target value`), 
      `Lower bound` = ifelse(`Lower bound` < 0, 0, `Lower bound`), 
      `Upper bound` = ifelse(`Upper bound` < 0, 0, `Upper bound`)
    ) %>% mutate(
      `Target value` = ifelse(`Target value` > 1, 1, `Target value`), 
      `Lower bound` = ifelse(`Lower bound` > 1, 1, `Lower bound`), 
      `Upper bound` = ifelse(`Upper bound` > 1, 1, `Upper bound`)
    )
  }
  
  tempDF <- tempDF %>% mutate(
    `Row value` = factor(`Row value`, levels=rev(levels(`Row value`)))
  ) 
  
  if(measureName=="Share >0"){
    tempDF <- tempDF %>% mutate(
      `For Tooltip`=paste(
        "Target variable: ", tempDF$`Target name`, '\n', 
        "Selected group: ", tempDF$`Row value`, '\n', 
        "Sector: ", tempDF$`Sector value`, '\n', 
        "Estimate: ", percent(tempDF$`Target value`, accuracy=0.1), '\n',
        "95% confidence interval: ", percent(tempDF$`Lower bound`, accuracy=0.1), " to ", percent(tempDF$`Upper bound`, accuracy=0.1), 
        sep=""
      )
    )
  }
  if(measureName %in% c("Median", "Average")){
    tempDF <- tempDF %>% mutate(
      `For Tooltip`=paste(
        "Target variable: ", tempDF$`Target name`, '\n', 
        "Selected group: ", tempDF$`Row value`, '\n', 
        "Sector: ", tempDF$`Sector value`, '\n', 
        "Estimate: ", dollar(tempDF$`Target value`, accuracy=1), '\n',
        "95% confidence interval: ", dollar(tempDF$`Lower bound`, accuracy=1), " to ", dollar(tempDF$`Upper bound`, accuracy=1), 
        sep=""
      )
    )
  }

  plot1 <- ggplot(
    data=tempDF, mapping=aes(x=`Target value`, y=`Row value`, fill=`Row value`, text=`For Tooltip`)
  ) + geom_point() + geom_errorbar(
    aes(xmin=`Lower bound`, xmax=`Upper bound`, width=0.2)
  ) + facet_grid(
    `Sector value` ~ .
  ) + labs(
    x=tempDF$`Title name`[1], y=""
  )
  
  if(measureName=="Share >0"){
    plot1 <- plot1 + scale_x_continuous(
      labels=percent_format(accuracy=1), limits=c(-0.03, 1.03), breaks=c(0, 0.25, 0.5, 0.75, 1)
    ) 
  }
  if(measureName %in% c("Median", "Average")){
    plot1 <- plot1 + scale_x_continuous(
      labels=dollar_format(accuracy=1, limits=c(
        tempDF$`Lower bound for axis`[1], 
        tempDF$`Upper bound for axis`[1]
      ))
    ) 
  }

  return(ggplotly(plot1, tooltip="text"))
  
  rm(plot1, tempDF)

}

```

```{r chartFn2, include=FALSE}

chartFn2 <- function(distributionName, rowName){
  
  # distributionName <- "Income Quartile"
  # rowName <- "Parents' Highest Education Level"
  
  tempDF <- DIST.SECTOR3 %>% filter(
    `Distribution name`==distributionName, 
    `Row name`==rowName
  )
  
  tempDF <- tempDF %>% mutate(
    `Share` = `Share` / 100, 
    `Lower bound` = `Lower bound` / 100, 
    `Upper bound` = `Upper bound` / 100
  ) %>% mutate(
    `Share` = ifelse(`Share` < 0, 0, `Share`), 
    `Lower bound` = ifelse(`Lower bound` < 0, 0, `Lower bound`), 
    `Upper bound` = ifelse(`Upper bound` < 0, 0, `Upper bound`)
  ) %>% mutate(
    `Share` = ifelse(`Share` > 1, 1, `Share`), 
    `Lower bound` = ifelse(`Lower bound` > 1, 1, `Lower bound`), 
    `Upper bound` = ifelse(`Upper bound` > 1, 1, `Upper bound`)
  )
  
  # Confirm whether this is needed:
  tempDF <- tempDF %>% mutate(
    `Row value` = factor(`Row value`, levels=rev(levels(`Row value`)))
  ) 
  
  tempDF <- tempDF %>% mutate(
    `For Tooltip`=paste(
      "Distribution variable: ", tempDF$`Distribution name`, '\n', 
      "Selected group: ", tempDF$`Row value`, '\n', 
      "Sector: ", tempDF$`Sector value`, '\n', 
      "Estimate: ", percent(tempDF$`Share`, accuracy=0.1), '\n',
      "95% confidence interval: ", percent(tempDF$`Lower bound`, accuracy=0.1), " to ", percent(tempDF$`Upper bound`, accuracy=0.1), 
      sep=""
    )
  )
  
  plot1 <- ggplot(
    data=tempDF, mapping=aes(x=`Share`, y=`Row value`, fill=`Category name`, text=`For Tooltip`)
  ) + geom_bar(
    position="stack", stat="identity"
  ) + facet_grid(
    `Sector value` ~ .
  ) + labs(
    x=paste("Distribution of ", tempDF$`Distribution name`[1], " by ", tempDF$`Row name`[1]), y=""
  ) + theme(
    legend.position="top"
  ) + scale_x_continuous(labels=percent_format(accuracy=1))
  
  plot1 <- ggplotly(
    plot1, tooltip="text"
  ) %>% layout(legend = list(
    orientation = "h",   # show entries horizontally
    xanchor = "center",  # use center of legend as anchor
    x = 0.5)             # put legend in center of x-axis
  )
  
  return(plot1)
  
  rm(plot1, tempDF)
  
}

```

```{r processing, include=FALSE}

#### Setup ####

library(scales)
library(plotly)
library(tidyverse)
library(kableExtra)

setwd("/Users/peter_granville/Net Price Equity")

#### End #### 

#### Write function to load averages, percentages, and shares above zero ####

loadDatalab1 <- function(
  sectionName, 
  retrievalCode, 
  sectorValRow, 
  dataStart, 
  dataEnd 
){
  
  dataLength <- dataEnd - dataStart + 1
  
  workingDir <- paste("/Users/peter_granville/Net Price Equity/NPSAS Data/", sectionName, sep="")
  setwd(workingDir)
  rm(workingDir)
  
  fileList <- list.files(getwd())
  correctFileName <- NA
  for(i in (1:length(fileList))){
    tempDF <- read.csv(fileList[i], header=FALSE)
    if(grepl(retrievalCode, tempDF$V1[nrow(tempDF)])){
      correctFileName <- fileList[i]
    }
    rm(tempDF)
  }
  rm(i, fileList)
  
  if(is.na(correctFileName)){
    stop("File with retrieval code not found")
  }else{
    
    dataDF <- read.csv(
      file=correctFileName,
      skip=dataStart-1, 
      nrows=dataLength,
      header=FALSE
    )
    rm(dataLength)
    
    sectorValDF <- read.csv(
      file=correctFileName, 
      skip=sectorValRow-1, 
      nrows=1,
      header=FALSE
    )
    
    sectorName <- sectorValDF$V1[1]
    rm(sectorValDF)
    
    targetName <- dataDF$V2[1]
    
    if(dataDF$V2[2]== "0 <= X <= 0"){ 
      # Percentages
      measureName <- "Share >0"
      rowName <- dataDF$V1[5]
      dataDF <- dataDF %>% select(-`V2`) %>% select(-`V3`)
      if("100%" %in% dataDF$`V6`){dataDF <- dataDF %>% select(-`V6`)}
      dataDF <- dataDF %>% filter(
        (`V1` != "") & (`V4` != "")
      )
      dataDF <- dataDF %>% rename(
        `V2` = `V4`, 
        `V3` = `V5`
      )
    }else{
      # Averages or Medians 
      measureName <- dataDF$V2[2]
      rowName <- dataDF$V1[5]
      measureName <- gsub("[() ]", "", measureName)
      dataDF <- dataDF %>% filter(
        (`V1` != "") & (`V2` != "")
      )
    }

    if((measureName %in% c("Average", "Median", "Share >0"))==FALSE){
      stop("The measure detetcted is not average, median, or share above 0. Use different function.")
    }else{
      dataDF <- dataDF %>% rename(
        `Row value` = `V1`, 
        `Target value` = `V2`, 
        `Target confidence interval` = `V3`
      ) %>% mutate(
        `Sector value` = rep(sectorName), 
        `Target name` = rep(targetName), 
        `Row name` = rep(rowName),
        `Measure name` = rep(measureName), 
        `Source code` = rep(retrievalCode), 
        `Section name` = rep(sectionName)
      )
      return(dataDF)
      rm(dataDF, sectorName, targetName, rowName, measureName, correctFile)
    }
  }
}

#### End #### 

#### Write function to load for % distributions ####

loadDatalab2 <- function(
    sectionName, 
    retrievalCode, 
    sectorValRow, 
    dataStart, 
    dataEnd 
){
  
  dataLength <- dataEnd - dataStart + 1
  
  workingDir <- paste("/Users/peter_granville/Net Price Equity/NPSAS Data/", sectionName, sep="")
  setwd(workingDir)
  rm(workingDir)
  
  fileList <- list.files(getwd())
  correctFileName <- NA
  for(i in (1:length(fileList))){
    tempDF <- read.csv(fileList[i], header=FALSE)
    if(grepl(retrievalCode, tempDF$V1[nrow(tempDF)])){
      correctFileName <- fileList[i]
    }
    rm(tempDF)
  }
  rm(i, fileList)
  
  if(is.na(correctFileName)){
    stop("File with retrieval code not found")
  }else{
    
    dataDF <- read.csv(
      file=correctFileName,
      skip=dataStart-1, 
      nrows=dataLength,
      header=FALSE
    )
    rm(dataLength)
    
    sectorValDF <- read.csv(
      file=correctFileName, 
      skip=sectorValRow-1, 
      nrows=1,
      header=FALSE
    )
    
    sectorName <- sectorValDF$V1[1]
    rm(sectorValDF)
    
    distributionName <- dataDF$V2[1]
    if(sectionName=="D10 Percentages"){
      rowName <- "Overall"
    }else{
      rowName <- dataDF$V1[5]
    }
    nDist <- (ncol(dataDF) - 2) / 2
    
    if(nDist==2){
      if("100%" %in% dataDF$`V6`){dataDF <- dataDF %>% select(-`V6`)}
      distCategoryName1 <- dataDF$V2[2] 
      distCategoryName2 <- dataDF$V4[2] 
    }
    if(nDist==3){
      if("100%" %in% dataDF$`V8`){dataDF <- dataDF %>% select(-`V8`)}
      distCategoryName1 <- dataDF$V2[2] 
      distCategoryName2 <- dataDF$V4[2] 
      distCategoryName3 <- dataDF$V6[2] 
      
    }
    if(nDist==4){
      if("100%" %in% dataDF$`V10`){dataDF <- dataDF %>% select(-`V10`)}
      distCategoryName1 <- dataDF$V2[2] 
      distCategoryName2 <- dataDF$V4[2] 
      distCategoryName3 <- dataDF$V6[2] 
      distCategoryName4 <- dataDF$V8[2] 
    }
    if(nDist==5){
      if("100%" %in% dataDF$`V12`){dataDF <- dataDF %>% select(-`V12`)}
      distCategoryName1 <- dataDF$V2[2] 
      distCategoryName2 <- dataDF$V4[2] 
      distCategoryName3 <- dataDF$V6[2] 
      distCategoryName4 <- dataDF$V8[2] 
      distCategoryName5 <- dataDF$V10[2] 
    }
    if(nDist==6){
      if("100%" %in% dataDF$`V14`){dataDF <- dataDF %>% select(-`V14`)}
      distCategoryName1 <- dataDF$V2[2] 
      distCategoryName2 <- dataDF$V4[2] 
      distCategoryName3 <- dataDF$V6[2] 
      distCategoryName4 <- dataDF$V8[2] 
      distCategoryName5 <- dataDF$V10[2] 
      distCategoryName6 <- dataDF$V12[2] 
    }
    if(nDist==7){
      if("100%" %in% dataDF$`V16`){dataDF <- dataDF %>% select(-`V16`)}
      distCategoryName1 <- dataDF$V2[2] 
      distCategoryName2 <- dataDF$V4[2] 
      distCategoryName3 <- dataDF$V6[2] 
      distCategoryName4 <- dataDF$V8[2] 
      distCategoryName5 <- dataDF$V10[2] 
      distCategoryName6 <- dataDF$V12[2] 
      distCategoryName7 <- dataDF$V14[2] 
    }

    dataDF <- dataDF %>% filter(
      `V1` != "", 
      `V2` != ""
    ) %>% rename(
      `Row value` = `V1`,
      `Category 1 share` = `V2`, 
      `Category 1 interval` = `V3`,
      `Category 2 share` = `V4`, 
      `Category 2 interval` = `V5`
    )
    categoryNamesDF <- data.frame(
      `Category number` = character(), 
      `Category name` = character(), 
      check.names=FALSE
    ) %>% add_row(
      `Category number` = "Category 1", 
      `Category name` = distCategoryName1
    ) %>% add_row(
      `Category number` = "Category 2", 
      `Category name` = distCategoryName2
    )
    if(nDist >= 3){
      dataDF <- dataDF %>% rename(
        `Category 3 share` = `V6`, 
        `Category 3 interval` = `V7`
      )
      categoryNamesDF <- categoryNamesDF %>% add_row(
        `Category number` = "Category 3", 
        `Category name` = distCategoryName3
      )
    }
    if(nDist >= 4){
      dataDF <- dataDF %>% rename(
        `Category 4 share` = `V8`, 
        `Category 4 interval` = `V9`
      )
      categoryNamesDF <- categoryNamesDF %>% add_row(
        `Category number` = "Category 4", 
        `Category name` = distCategoryName4
      )
    }
    if(nDist >= 5){
      dataDF <- dataDF %>% rename(
        `Category 5 share` = `V10`, 
        `Category 5 interval` = `V11`
      )
      categoryNamesDF <- categoryNamesDF %>% add_row(
        `Category number` = "Category 5", 
        `Category name` = distCategoryName5
      )
    }
    if(nDist >= 6){
      dataDF <- dataDF %>% rename(
        `Category 6 share` = `V12`, 
        `Category 6 interval` = `V13`
      )
      categoryNamesDF <- categoryNamesDF %>% add_row(
        `Category number` = "Category 6", 
        `Category name` = distCategoryName6
      )
    }
    if(nDist >= 7){
      dataDF <- dataDF %>% rename(
        `Category 7 share` = `V14`, 
        `Category 7 interval` = `V15`
      )
      categoryNamesDF <- categoryNamesDF %>% add_row(
        `Category number` = "Category 7", 
        `Category name` = distCategoryName7
      )
    }
    
    sharesDF <- dataDF %>% select(
      `Row value`, 
      any_of(c(
        "Category 1 share", 
        "Category 2 share", 
        "Category 3 share", 
        "Category 4 share", 
        "Category 5 share", 
        "Category 6 share", 
        "Category 7 share"
      ))
    ) %>% pivot_longer(
      cols=any_of(c(
        "Category 1 share", 
        "Category 2 share", 
        "Category 3 share", 
        "Category 4 share", 
        "Category 5 share", 
        "Category 6 share", 
        "Category 7 share"
      )), 
      names_to="Category number", 
      values_to="Share"
    )
    intervalsDF <- dataDF %>% select(
      `Row value`, 
      any_of(c(
        "Category 1 interval", 
        "Category 2 interval", 
        "Category 3 interval", 
        "Category 4 interval", 
        "Category 5 interval", 
        "Category 6 interval", 
        "Category 7 interval"
      ))
    ) %>% pivot_longer(
      cols=any_of(c(
        "Category 1 interval", 
        "Category 2 interval", 
        "Category 3 interval", 
        "Category 4 interval", 
        "Category 5 interval", 
        "Category 6 interval", 
        "Category 7 interval"
      )), 
      names_to="Category number", 
      values_to="Interval"
    )
    
    sharesDF$`Category number` <- gsub(" share", "", sharesDF$`Category number`)
    intervalsDF$`Category number` <- gsub(" interval", "", intervalsDF$`Category number`)
    
    dataDF <- full_join(x=sharesDF, y=intervalsDF, by=c("Row value", "Category number"))
    rm(sharesDF, intervalsDF)
    
    dataDF <- left_join(x=dataDF, y=categoryNamesDF, by="Category number")
    rm(categoryNamesDF)
    
    totalCategories <- length(unique(dataDF$`Category number`))
    
    dataDF <- dataDF %>% mutate(
      `Sector value` = rep(sectorName), 
      `Distribution name` = rep(distributionName), 
      `Number of categories` = rep(totalCategories),
      `Row name` = rep(rowName),
      `Source code` = rep(retrievalCode), 
      `Section name` = rep(sectionName)
    )
    return(dataDF)
    rm(dataDF, sectorName, distributionName, rowName, measureName, correctFile, totalCategories)
  }
}

#### End #### 

#### Write function to identify retrieval code, sectorRowVal, dataStart, and dataEnd from files ####

fileScan <- function(fileName, folderName, subtableSelect){
  
  returnDF <- data.frame(
    `folder` = character(), 
    `subtable` = character(), 
    `retrievalCode` = character(), 
    `sectorRowVal` = numeric(), 
    `dataStart` = numeric(), 
    `dataEnd` = numeric()
  )
  
  workingDir <- paste("/Users/peter_granville/Net Price Equity/NPSAS Data/", folderName, sep="")
  setwd(workingDir)
  rm(workingDir)
  
  tempDF <- read.csv(fileName, header=FALSE, blank.lines.skip=FALSE, col.names=paste("V", (1:20), sep="")) 
  tempDF <- tempDF %>% mutate(
    `Original row number` = (1:nrow(tempDF))
  )
  
  retrievalCodeLine <- tempDF$V1[nrow(tempDF)]
  retrievalCodeLine <- gsub("The code to retrieve results is ", "", retrievalCodeLine)
  retrievalCodeLine <- gsub("[.]", "", retrievalCodeLine)
  
  backstopLine <- tempDF %>% filter(
    (grepl("! Interpret", `V1`)) | (grepl("Reporting standards", `V1`)) | (grepl("The names of the variables", `V1`)) | (grepl("The weight variable used", `V1`))
  )
  backstopLine <- min(backstopLine$`Original row number`, na.rm=TRUE)
  
  if(subtableSelect=="SECTOR3"){
    searchTerm <- "NPSAS institution sector"
  }else{
    if(subtableSelect=="INSTSTAT"){
      searchTerm <- "NPSAS institution state"
    }else{
      stop("Improper subtable selection")
    }
  }
  
  sectorLabels <- tempDF %>% filter(
    grepl(searchTerm, `V1`)==TRUE, 
    grepl("Filtered by", `V1`)==FALSE
  )
  rm(searchTerm)
  sectorLabels <- sectorLabels$`Original row number`

  intervalLabels <- tempDF %>% filter(
    grepl("CONFIDENCE INTERVALS", `V1`)==TRUE, 
  )
  intervalLabels <- intervalLabels$`Original row number`
  
  if(length(sectorLabels) != length(intervalLabels)){
    stop("Error")
  }else{
    for(i in (1:length(sectorLabels))){
      startOfSet <- intervalLabels[i]
      if(i==length(sectorLabels)){
        endOfSet <- backstopLine
      }else{
        endOfSet <- sectorLabels[i+1]
      }
      if(tempDF$V1[endOfSet - 1]==""){endOfSet <- endOfSet - 1}
      returnDF <- returnDF %>% add_row(
        `folder` = folderName,
        `subtable` = subtableSelect,
        `retrievalCode` = retrievalCodeLine, 
        `sectorRowVal` = sectorLabels[i], 
        `dataStart` = startOfSet + 1, 
        `dataEnd` = endOfSet - 1
      )
      rm(startOfSet, endOfSet)
    }
    rm(i)
  }
  
  return(returnDF)
  rm(backstopLine, intervalLabels, sectorLabels, retrievalCodeLine, tempDF, returnDF)
}

#### End #### 

#### Write function to identify key info from all files in a folder ####

folderScan <- function(folderName0, subtableSelect0){
  
  workingDir <- paste("/Users/peter_granville/Net Price Equity/NPSAS Data/", folderName0, sep="")
  setwd(workingDir)
  rm(workingDir)
  
  fileList <- list.files(getwd())
  
  for(i in (1:length(fileList))){
    
    tempDF <- fileScan(fileName=fileList[i], folderName=folderName0, subtableSelect=subtableSelect0)
    if(i==1){
      returnDF <- tempDF
    }else{
      returnDF <- rbind(returnDF, tempDF)
    }
    rm(tempDF)
    
  }
  rm(i)
  
  return(returnDF)
  rm(fileList)
}

#### End #### 

#### Write function to pull all the prior functions together ####

runAllFunctions <- function(foldersForProcessing, functionSelection, subtableSelection){
  
  for(i in (1:length(foldersForProcessing))){
    
    print(paste("Running folder ", foldersForProcessing[i], ".", sep=""))
    runThese <- folderScan(folderName0=foldersForProcessing[i], subtableSelect0=subtableSelection)
    for(j in (1:nrow(runThese))){
      
      if(functionSelection=="loadDatalab1"){
        innerEnvelope <- loadDatalab1(
          sectionName = runThese$folder[j], 
          retrievalCode = runThese$retrievalCode[j], 
          sectorValRow = runThese$sectorRowVal[j], 
          dataStart = runThese$dataStart[j], 
          dataEnd = runThese$dataEnd[j]
        )
      }else{
        if(functionSelection=="loadDatalab2"){
          innerEnvelope <- loadDatalab2(
            sectionName = runThese$folder[j], 
            retrievalCode = runThese$retrievalCode[j], 
            sectorValRow = runThese$sectorRowVal[j], 
            dataStart = runThese$dataStart[j], 
            dataEnd = runThese$dataEnd[j]
          )
        }else{
          stop("Error")
        }
      }
      if(j==1){
        middleEnvelope <- innerEnvelope
      }else{
        middleEnvelope <- rbind(middleEnvelope, innerEnvelope)
      }
      rm(innerEnvelope)
    }
    rm(j)
    
    if(i==1){
      outerEnvelope <- middleEnvelope
    }else{
      outerEnvelope <- rbind(outerEnvelope, middleEnvelope)
    }
    rm(middleEnvelope)
  }
  rm(i)
  
  return(outerEnvelope)
  rm(outerEnvelope)
}

#### End #### 

################################################
#### Disaggregated by SECTOR3               ####
################################################

#### Averages, Medians, Percents (loadDatalab1) ####

AMP.SECTOR3 <- runAllFunctions(foldersForProcessing=c(
  "A1 Averages", 
  "A1 Percentages", 
  "A2 Averages", 
  "A2 Percentages", 
  "A3 Averages",    
  "A3 Percentages", 
  "A4 Averages", 
  "A4 Percentages", 
  "A5 Averages", 
  "A5 Percentages", 
  "A6 Averages", 
  "A6 Percentages", 
  "A7 Averages", 
  "A7 Percentages", 
  "A8 Averages",     
  "A8 Percentages", 
  "A9 Averages", 
  "A9 Percentages", 
  "A10 Averages", 
  "A10 Percentages", 
  "A11 Averages", 
  "A11 Percentages", 
  "B1 Medians", 
  "C1 Averages", 
  "C1 Percentages", 
  "C2 Averages", 
  "C2 Medians", 
  "C3 Averages",     
  "C3 Medians", 
  "C3 Percentages", 
  "C4 Medians", 
  "C5 Medians", 
  "C6 Medians", 
  "C7 Medians" 
), functionSelection="loadDatalab1", subtableSelection="SECTOR3")

#### End #### 

#### Distributions (loadDatalab2) ####

DIST.SECTOR3 <- runAllFunctions(foldersForProcessing=c(
  "B2 Percentages",  
  "D1 Percentages", 
  "D2 Percentages", 
  "D3 Percentages", 
  "D4 Percentages", 
  "D5 Percentages", 
  "D6 Percentages", 
  "D7 Percentages", 
  "D8 Percentages", 
  "D9 Percentages", 
  "D10 Percentages"
), functionSelection="loadDatalab2", subtableSelection="SECTOR3")

#### End #### 

################################################
#### Disaggregated by INSTSTAT: Four-years  ####
################################################

#### Averages, Medians, Percents (loadDatalab1) ####

AMP.INSTSTAT.4Y <- runAllFunctions(foldersForProcessing=c(
  "E1 Averages",
  "E1 Percentages",
  "E2 Averages",
  "E2 Percentages",
  "E3 Medians",
  "E4 Medians",
  "E5 Medians"
), functionSelection="loadDatalab1", subtableSelection="INSTSTAT")

#### End #### 

################################################
#### Disaggregated by INSTSTAT: Two-years   ####
################################################

#### Averages, Medians, Percents (loadDatalab1) ####

AMP.INSTSTAT.2Y <- runAllFunctions(foldersForProcessing=c(
  "F1 Averages", 
  "F1 Percentages", 
  "F2 Averages",
  "F2 Percentages", 
  "F3 Medians", 
  "F4 Medians", 
  "F5 Medians"
), functionSelection="loadDatalab1", subtableSelection="INSTSTAT")

#### End #### 

################################################
#### Store data files                       ####
################################################

#### Small adjustments ####

AMP.INSTSTAT.2Y <- AMP.INSTSTAT.2Y %>% rename(`State` = `Sector value`)
AMP.INSTSTAT.4Y <- AMP.INSTSTAT.4Y %>% rename(`State` = `Sector value`)

#### End #### 

#### Retitle row names ####

AMP.SECTOR3 <- AMP.SECTOR3 %>% mutate(
  `Row name` = ifelse(`Row name`=="Expected Family Contribution", "Zero EFC Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Federal Pell Grant", "Pell Recipient Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Historical black college indicator", "Institution HBCU Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Income quartile (administrative collection)", "Income Quartile", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Minority Serving Institution indicator", "Institution MSI Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="NPSAS institution state", "Institution State", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Parents' highest education level (administrative collection)", "Parents' Highest Education Level", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Race/ethnicity (with multiple)", "Race/Ethnicity", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Selectivity (All 4-year institutions)", "Institution Selectivity", `Row name`)
) %>% mutate(
  `Sector value` = gsub("NPSAS institution sector - 3 categories - ", "", `Sector value`)
)

DIST.SECTOR3 <- DIST.SECTOR3 %>% mutate(
  `Row name` = ifelse(`Row name`=="Expected Family Contribution", "Zero EFC Status", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="Expected Family Contribution", "Zero EFC Status", `Distribution name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Federal Pell Grant", "Pell Recipient Status", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="Federal Pell Grant", "Pell Recipient Status", `Distribution name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Historical black college indicator", "Institution HBCU Status", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="Historical black college indicator", "Institution HBCU Status", `Distribution name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Income quartile (administrative collection)", "Income Quartile", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="Income quartile (administrative collection)", "Income Quartile", `Distribution name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Minority Serving Institution indicator", "Institution MSI Status", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="Minority Serving Institution indicator", "Institution MSI Status", `Distribution name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="NPSAS institution state", "Institution State", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="NPSAS institution state", "Institution State", `Distribution name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Parents' highest education level (administrative collection)", "Parents' Highest Education Level", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="Parents' highest education level (administrative collection)", "Parents' Highest Education Level", `Distribution name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Race/ethnicity (with multiple)", "Race/Ethnicity", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="Race/ethnicity (with multiple)", "Race/Ethnicity", `Distribution name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Selectivity (All 4-year institutions)", "Institution Selectivity", `Row name`), 
  `Distribution name` = ifelse(`Distribution name`=="Selectivity (All 4-year institutions)", "Institution Selectivity", `Distribution name`)
) %>% mutate(
  `Distribution name` = ifelse(`Distribution name`=="Grade point average in high school (dependent students)", "High School GPA", `Distribution name`)
) %>% mutate(
  `Sector value` = gsub("NPSAS institution sector - 3 categories - ", "", `Sector value`)
)

AMP.INSTSTAT.2Y <- AMP.INSTSTAT.2Y %>% mutate(
  `Row name` = ifelse(`Row name`=="Expected Family Contribution", "Zero EFC Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Federal Pell Grant", "Pell Recipient Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Historical black college indicator", "Institution HBCU Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Income quartile (administrative collection)", "Income Quartile", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Minority Serving Institution indicator", "Institution MSI Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="NPSAS institution state", "Institution State", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Parents' highest education level (administrative collection)", "Parents' Highest Education Level", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Race/ethnicity (with multiple)", "Race/Ethnicity", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Selectivity (All 4-year institutions)", "Institution Selectivity", `Row name`)
) %>% mutate(
  `State` = gsub("NPSAS institution state - ", "", `State`)
)

AMP.INSTSTAT.4Y <- AMP.INSTSTAT.4Y %>% mutate(
  `Row name` = ifelse(`Row name`=="Expected Family Contribution", "Zero EFC Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Federal Pell Grant", "Pell Recipient Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Historical black college indicator", "Institution HBCU Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Income quartile (administrative collection)", "Income Quartile", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Minority Serving Institution indicator", "Institution MSI Status", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="NPSAS institution state", "Institution State", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Parents' highest education level (administrative collection)", "Parents' Highest Education Level", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Race/ethnicity (with multiple)", "Race/Ethnicity", `Row name`)
) %>% mutate(
  `Row name` = ifelse(`Row name`=="Selectivity (All 4-year institutions)", "Institution Selectivity", `Row name`)
) %>% mutate(
  `State` = gsub("NPSAS institution state - ", "", `State`)
)

#### End #### 

#### Rename row values ####

rowValueRename <- AMP.SECTOR3 %>% mutate(`Count` = rep(1))
rowValueRename <- aggregate(
  data=rowValueRename, `Count` ~ `Row value` + `Row name`, FUN=sum
) %>% select(
  -(`Count`)
)
rowValueRename <- rowValueRename %>% mutate(
  `New value` = `Row value`
) %>% mutate(
  `New value` = ifelse((`Row value`=="Yes") & (`Row name`=="Institution HBCU Status"), "HBCUs", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="No") & (`Row name`=="Institution HBCU Status"), "Non-HBCUs", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="American Indian/Alaska Native-serving") & (`Row name`=="Institution MSI Status"), "Tribal college", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="Asian/Native Hawaiian/Pacific Islander-serving") & (`Row name`=="Institution MSI Status"), "AAPISI", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="Black/African American-serving, non-HBCU") & (`Row name`=="Institution MSI Status"), "PBI", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="Hispanic/Latino-serving") & (`Row name`=="Institution MSI Status"), "HSI", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="Non-minority serving") & (`Row name`=="Institution MSI Status"), "Not an MSI", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="Other minority-serving") & (`Row name`=="Institution MSI Status"), "Other MSI", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="0 <= X <= 0") & (`Row name`=="Pell Recipient Status"), "Not a Pell recipient", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="1 <= X <= 9293") & (`Row name`=="Pell Recipient Status"), "Pell recipient", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="American Indian or Alaska Native") & (`Row name`=="Race/Ethnicity"), "Native American", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="Native Hawaiian/other Pacific Islander") & (`Row name`=="Race/Ethnicity"), "Native Hawaiian/Pacific Islander", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="0 <= X <= 0") & (`Row name`=="Zero EFC Status"), "Zero EFC", `New value`)
) %>% mutate(
  `New value` = ifelse((`Row value`=="1 <= X <= 1000000") & (`Row name`=="Zero EFC Status"), "Nonzero EFC", `New value`)
) 

AMP.SECTOR3 <- left_join(
  x=AMP.SECTOR3, y=rowValueRename, by=c("Row value", "Row name")
) %>% select(
  -(`Row value`)
) %>% rename(
  `Row value` = `New value`
)

AMP.INSTSTAT.2Y <- left_join(
  x=AMP.INSTSTAT.2Y, y=rowValueRename, by=c("Row value", "Row name")
) %>% select(
  -(`Row value`)
) %>% rename(
  `Row value` = `New value`
)

AMP.INSTSTAT.4Y <- left_join(
  x=AMP.INSTSTAT.4Y, y=rowValueRename, by=c("Row value", "Row name")
) %>% select(
  -(`Row value`)
) %>% rename(
  `Row value` = `New value`
)

DIST.SECTOR3 <- left_join(
  x=DIST.SECTOR3, y=rowValueRename, by=c("Row value", "Row name")
) %>% select(
  -(`Row value`)
) %>% rename(
  `Row value` = `New value`
)

#### End #### 

#### Rename category names for distributions ####

categoryNameRename <- rowValueRename %>% rename(
  `Category name` = `Row value`, 
  `Distribution name` = `Row name`
) %>% add_row(
  `Category name`="0.5-0.9 (D- to D)", `Distribution name`="High School GPA", `New value`="0.5 to 0.9"
) %>% add_row(
  `Category name`="1.0-1.4 (D to C-)", `Distribution name`="High School GPA", `New value`="1.0 to 1.4"
) %>% add_row(
  `Category name`="1.5-1.9 (C- to C)", `Distribution name`="High School GPA", `New value`="1.5 to 1.9"
) %>% add_row(
  `Category name`="2.0-2.4 (C to B-)", `Distribution name`="High School GPA", `New value`="2.0 to 2.4"
) %>% add_row(
  `Category name`="2.5-2.9 (B- to B)", `Distribution name`="High School GPA", `New value`="2.5 to 2.9"
) %>% add_row(
  `Category name`="3.0-3.4 (B to A-)", `Distribution name`="High School GPA", `New value`="3.0 to 3.4"
) %>% add_row(
  `Category name`="3.5-4.0 (A- to A)", `Distribution name`="High School GPA", `New value`="3.5 to 4.0"
)

DIST.SECTOR3 <- left_join(
  x=DIST.SECTOR3, y=categoryNameRename, by=c("Distribution name", "Category name")
) %>% select(
  -(`Category name`)
) %>% rename(
  `Category name` = `New value`
)

rm(categoryNameRename, rowValueRename)

#### End #### 

#### Write files ####

setwd("/Users/peter_granville/Net Price Equity")

write.csv(AMP.INSTSTAT.2Y, "AMP-INSTSTAT-2Y.csv", row.names=FALSE)
write.csv(AMP.INSTSTAT.4Y, "AMP-INSTSTAT-4Y.csv", row.names=FALSE)
write.csv(AMP.SECTOR3, "AMP-SECTOR3.csv", row.names=FALSE)
write.csv(DIST.SECTOR3, "DIST-SECTOR3.csv", row.names=FALSE)

#### End #### 

#### List unique tables ####

AMP.SECTOR3 <- AMP.SECTOR3 %>% mutate(
  `Table ID 1` = paste(`Target name`, sep=" | "),
  `Table ID 2` = paste(`Target name`, `Row name`, sep=" | "),
  `Table ID 3` = paste(`Target name`, `Row name`, `Measure name`, sep=" | "),
  `Table ID 4` = paste(`Target name`, `Row name`, `Measure name`, `Sector value`, sep=" | ")
)
length(unique(AMP.SECTOR3$`Table ID 1`))
length(unique(AMP.SECTOR3$`Table ID 2`))
length(unique(AMP.SECTOR3$`Table ID 3`))
length(unique(AMP.SECTOR3$`Table ID 4`))

DIST.SECTOR3 <- DIST.SECTOR3 %>% mutate(
  `Table ID 1` = paste(`Distribution name`, sep=" | "),
  `Table ID 2` = paste(`Distribution name`, `Row name`, sep=" | "),
  `Table ID 3` = paste(`Distribution name`, `Row name`, `Sector value`, sep=" | ")
)
length(unique(DIST.SECTOR3$`Table ID 1`))
length(unique(DIST.SECTOR3$`Table ID 2`))
length(unique(DIST.SECTOR3$`Table ID 3`))

AMP.INSTSTAT.2Y <- AMP.INSTSTAT.2Y %>% mutate(
  `Table ID 1` = paste(`Target name`, sep=" | "),
  `Table ID 2` = paste(`Target name`, `Row name`, sep=" | "),
  `Table ID 3` = paste(`Target name`, `Row name`, `Measure name`, sep=" | "),
  `Table ID 4` = paste(`Target name`, `Row name`, `Measure name`, `State`, sep=" | ")
)
length(unique(AMP.INSTSTAT.2Y$`Table ID 1`))
length(unique(AMP.INSTSTAT.2Y$`Table ID 2`))
length(unique(AMP.INSTSTAT.2Y$`Table ID 3`))
length(unique(AMP.INSTSTAT.2Y$`Table ID 4`))

AMP.INSTSTAT.4Y <- AMP.INSTSTAT.4Y %>% mutate(
  `Table ID 1` = paste(`Target name`, sep=" | "),
  `Table ID 2` = paste(`Target name`, `Row name`, sep=" | "),
  `Table ID 3` = paste(`Target name`, `Row name`, `Measure name`, sep=" | "),
  `Table ID 4` = paste(`Target name`, `Row name`, `Measure name`, `State`, sep=" | ")
)
length(unique(AMP.INSTSTAT.4Y$`Table ID 1`))
length(unique(AMP.INSTSTAT.4Y$`Table ID 2`))
length(unique(AMP.INSTSTAT.4Y$`Table ID 3`))
length(unique(AMP.INSTSTAT.4Y$`Table ID 4`))

#### End #### 

#### Create factor lists ####

levels.SectorValue <- c(
  "Total", 
  "Public 4-year",
  "Public 2-year", 
  "Other"
)

levels.TargetName <- c(
  "Federal Pell Grant",
  "Federal campus-based aid (SEOG, FWS)",
  "Title IV loans (includes Parent PLUS Loans)",
  "State grants total",
  "Institution grants total",
  "Private source grants",
  "State non-need & merit grants",
  "State need-based grants",
  "Institution non-need & merit grants",
  "Institutional need-based grants",
  "Total state and institutional grants",
  "Grant amount exceeding federal need",
  "Tuition and fees minus all grants",
  "Net tuition after all grants as percent of income",
  "Student budget minus all grants",
  "Net price after grants as percent of income",
  "Expected Family Contribution",
  "Tuition and fees paid",
  "Student budget (attendance adjusted)"
)

levels.RowName <- c(
  "Overall",
  "Income Quartile", 
  "Zero EFC Status", 
  "Pell Recipient Status", 
  "Parents' Highest Education Level", 
  "Race/Ethnicity", 
  "Institution HBCU Status", 
  "Institution MSI Status", 
  "Institution Selectivity", 
  "Institution State"
)

levels.MeasureName <- c(
  "Share >0", 
  "Average", 
  "Median"
)

levels.RowValue <- c(
  
  "Total",
  
  # Income Quartile
  "Top quartile",
  "Upper-middle quartile",
  "Lower-middle quartile",
  "Bottom quartile",
  
  # Institution HBCU Status
  "HBCUs",
  "Non-HBCUs",
  
  # Institution MSI Status
  "AAPISI",
  "HBCU",
  "HSI",
  "PBI",
  "Tribal college",
  "Other MSI",
  "Not an MSI",
  
  # Institution Selectivity
  "Very selective",
  "Moderately selective",  
  "Minimally selective",
  "Open admission",
  "Not a 4-year institution",
  
  # Institution State
  "Alabama",
  "Alaska",
  "Arizona",
  "Arkansas",
  "California",
  "Colorado",
  "Connecticut",
  "Delaware",
  "District of Columbia",
  "Florida",
  "Georgia",
  "Hawaii",
  "Idaho",
  "Illinois",
  "Indiana",
  "Iowa",
  "Kansas",
  "Kentucky",
  "Louisiana",
  "Maine",
  "Maryland",
  "Massachusetts",
  "Michigan",
  "Minnesota",
  "Mississippi",
  "Missouri",
  "Montana",
  "Nebraska",
  "Nevada",
  "New Hampshire",
  "New Jersey",
  "New Mexico",
  "New York",
  "North Carolina",
  "North Dakota",
  "Ohio",
  "Oklahoma",
  "Oregon",
  "Pennsylvania",
  "Puerto Rico",
  "Rhode Island",
  "South Carolina",
  "South Dakota",
  "Tennessee",
  "Texas",
  "Utah",
  "Vermont",
  "Virginia",
  "Washington",
  "West Virginia",
  "Wisconsin",
  "Wyoming",
  
  # Parents' Highest Education Level
  "College or beyond",
  "High school",
  "Middle school/junior high",
  
  # Pell Recipient Status
  "Pell recipient",
  "Not a Pell recipient",
  
  # Race/Ethnicity
  "White",
  "Hispanic or Latino",
  "Black or African American",
  "Asian",
  "Native American",
  "Native Hawaiian/Pacific Islander",
  "More than one race",
  
  # Zero EFC Status
  "Zero EFC",
  "Nonzero EFC"
)

levels.DistributionName <- c(
  "Income Quartile", 
  "Zero EFC Status", 
  "Pell Recipient Status", 
  "Parents' Highest Education Level", 
  "Race/Ethnicity", 
  "High School GPA",
  "Institution HBCU Status", 
  "Institution MSI Status", 
  "Institution Selectivity" 
)

levels.CategoryName <- c(
  levels.RowValue, c(
    # High School GPA
    "0.5 to 0.9", 
    "1.0 to 1.4", 
    "1.5 to 1.9", 
    "2.0 to 2.4", 
    "2.5 to 2.9", 
    "3.0 to 3.4", 
    "3.5 to 4.0"
  )
)

levels.State <- c(
  "Total",
  "Alabama",
  "Alaska",
  "Arizona",
  "Arkansas",
  "California",
  "Colorado",
  "Connecticut",
  "Delaware",
  "District of Columbia",
  "Florida",
  "Georgia",
  "Hawaii",
  "Idaho",
  "Illinois",
  "Indiana",
  "Iowa",
  "Kansas",
  "Kentucky",
  "Louisiana",
  "Maine",
  "Maryland",
  "Massachusetts",
  "Michigan",
  "Minnesota",
  "Mississippi",
  "Missouri",
  "Montana",
  "Nebraska",
  "Nevada",
  "New Hampshire",
  "New Jersey",
  "New Mexico",
  "New York",
  "North Carolina",
  "North Dakota",
  "Ohio",
  "Oklahoma",
  "Oregon",
  "Pennsylvania",
  "Puerto Rico",
  "Rhode Island",
  "South Carolina",
  "South Dakota",
  "Tennessee",
  "Texas",
  "Utah",
  "Vermont",
  "Virginia",
  "Washington",
  "West Virginia",
  "Wisconsin",
  "Wyoming"
)

#### End #### 

#### Assign order of tables ####

AMP.SECTOR3 <- AMP.SECTOR3 %>% mutate(
  `Target name` = as.factor(`Target name`), 
  `Row name` = as.factor(`Row name`), 
  `Measure name` = as.factor(`Measure name`), 
  `Sector value` = as.factor(`Sector value`),
  `Row value` = as.factor(`Row value`)
) %>% mutate(
  `Target name` = factor(`Target name`, levels=levels.TargetName), 
  `Row name` = factor(`Row name`, levels=levels.RowName), 
  `Measure name` = factor(`Measure name`, levels=levels.MeasureName), 
  `Sector value` = factor(`Sector value`, levels=levels.SectorValue),
  `Row value` = factor(`Row value`, levels=levels.RowValue)
) %>% arrange(
  `Target name`, 
  `Row name`, 
  `Measure name`, 
  `Sector value`,
  `Row value`
)

DIST.SECTOR3 <- DIST.SECTOR3 %>% mutate(
  `Distribution name` = as.factor(`Distribution name`), 
  `Row name` = as.factor(`Row name`), 
  `Sector value` = as.factor(`Sector value`),
  `Category name` = as.factor(`Category name`), 
  `Row value` = as.factor(`Row value`)
) %>% mutate(
  `Distribution name` = factor(`Distribution name`, levels=levels.DistributionName), 
  `Row name` = factor(`Row name`, levels=levels.RowName), 
  `Sector value` = factor(`Sector value`, levels=levels.SectorValue),
  `Category name` = factor(`Category name`, levels=levels.CategoryName), 
  `Row value` = factor(`Row value`, levels=levels.RowValue)
) %>% arrange(
  `Distribution name`, 
  `Row name`, 
  `Sector value`,
  `Category name`, 
  `Row value`
)

AMP.INSTSTAT.2Y <- AMP.INSTSTAT.2Y %>% mutate(
  `Target name` = as.factor(`Target name`), 
  `Row name` = as.factor(`Row name`), 
  `Measure name` = as.factor(`Measure name`), 
  `State` = as.factor(`State`),
  `Row value` = as.factor(`Row value`)
) %>% mutate(
  `Target name` = factor(`Target name`, levels=levels.TargetName), 
  `Row name` = factor(`Row name`, levels=levels.RowName), 
  `Measure name` = factor(`Measure name`, levels=levels.MeasureName), 
  `State` = factor(`State`, levels=levels.State),
  `Row value` = factor(`Row value`, levels=levels.RowValue)
) %>% arrange(
  `Target name`, 
  `Row name`, 
  `Measure name`, 
  `State`,
  `Row value`
)

AMP.INSTSTAT.4Y <- AMP.INSTSTAT.4Y %>% mutate(
  `Target name` = as.factor(`Target name`), 
  `Row name` = as.factor(`Row name`), 
  `Measure name` = as.factor(`Measure name`), 
  `State` = as.factor(`State`),
  `Row value` = as.factor(`Row value`)
) %>% mutate(
  `Target name` = factor(`Target name`, levels=levels.TargetName), 
  `Row name` = factor(`Row name`, levels=levels.RowName), 
  `Measure name` = factor(`Measure name`, levels=levels.MeasureName), 
  `State` = factor(`State`, levels=levels.State),
  `Row value` = factor(`State`, levels=levels.RowValue)
) %>% arrange(
  `Target name`, 
  `Row name`, 
  `Measure name`, 
  `State`,
  `Row value`
)

#### End #### 

#### Print table IDs ####

# output1 <- AMP.SECTOR3 %>% filter(
#   duplicated(`Table ID 3`)==FALSE
# )
# output2 <- DIST.SECTOR3 %>% filter(
#   duplicated(`Table ID 2`)==FALSE
# )
# output3 <- AMP.INSTSTAT.2Y %>% filter(
#   duplicated(`Table ID 3`)==FALSE
# )
# output4 <- AMP.INSTSTAT.4Y %>% filter(
#   duplicated(`Table ID 3`)==FALSE
# )
# 
# write.csv(output1, "output1.csv", row.names=FALSE)
# write.csv(output2, "output2.csv", row.names=FALSE)
# write.csv(output3, "output3.csv", row.names=FALSE)
# write.csv(output4, "output4.csv", row.names=FALSE)

#### End #### 

```

# Section A: Nationwide distributions of financial aid 

## Unit A1: Distributions of aid programs 

### Federal Pell Grant

####  {.tabset}

##### By Income Quartile

###### Share receiving Federal Pell Grant by Income Quartile

```{r chunk51901809} 
chartFn1(targetName="Federal Pell Grant", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Income Quartile

```{r chunk34608388} 
chartFn1(targetName="Federal Pell Grant", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Federal Pell Grant by Zero EFC Status

```{r chunk12999968} 
chartFn1(targetName="Federal Pell Grant", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Zero EFC Status

```{r chunk50201470} 
chartFn1(targetName="Federal Pell Grant", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Federal Pell Grant by Pell Recipient Status

```{r chunk49240993} 
chartFn1(targetName="Federal Pell Grant", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Pell Recipient Status

```{r chunk87506682} 
chartFn1(targetName="Federal Pell Grant", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Federal Pell Grant by Parents' Highest Education Level

```{r chunk62476864} 
chartFn1(targetName="Federal Pell Grant", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Parents' Highest Education Level

```{r chunk28274931} 
chartFn1(targetName="Federal Pell Grant", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Federal Pell Grant by Race/Ethnicity

```{r chunk99839860} 
chartFn1(targetName="Federal Pell Grant", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Race/Ethnicity

```{r chunk48558864} 
chartFn1(targetName="Federal Pell Grant", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Federal Pell Grant by Institution HBCU Status

```{r chunk3722066} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Institution HBCU Status

```{r chunk70893955} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Federal Pell Grant by Institution MSI Status

```{r chunk4947001} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Institution MSI Status

```{r chunk50988928} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Federal Pell Grant by Institution Selectivity

```{r chunk10588420} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Institution Selectivity

```{r chunk84453019} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Federal Pell Grant by Institution State

```{r chunk92018076} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Institution State

```{r chunk93225442} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}
 
### Federal campus-based aid (SEOG, FWS)

####  {.tabset}

##### By Income Quartile

###### Share receiving Federal campus-based aid (SEOG, FWS) by Income Quartile

```{r chunk80796992} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Income Quartile

```{r chunk66753992} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Federal campus-based aid (SEOG, FWS) by Zero EFC Status

```{r chunk13320962} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Zero EFC Status

```{r chunk25654771} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Federal campus-based aid (SEOG, FWS) by Pell Recipient Status

```{r chunk17952826} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Pell Recipient Status

```{r chunk34566211} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Federal campus-based aid (SEOG, FWS) by Parents' Highest Education Level

```{r chunk15899056} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Parents' Highest Education Level

```{r chunk8396142} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Federal campus-based aid (SEOG, FWS) by Race/Ethnicity

```{r chunk67107596} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Race/Ethnicity

```{r chunk18498755} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Federal campus-based aid (SEOG, FWS) by Institution HBCU Status

```{r chunk81745155} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Institution HBCU Status

```{r chunk44965299} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Federal campus-based aid (SEOG, FWS) by Institution MSI Status

```{r chunk45950525} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Institution MSI Status

```{r chunk79514429} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Federal campus-based aid (SEOG, FWS) by Institution Selectivity

```{r chunk55571663} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Institution Selectivity

```{r chunk43163601} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Federal campus-based aid (SEOG, FWS) by Institution State

```{r chunk27577672} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Institution State

```{r chunk25350575} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Title IV loans (includes Parent PLUS Loans)

####  {.tabset}

##### By Income Quartile

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Income Quartile

```{r chunk56592274} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Income Quartile

```{r chunk43183158} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Zero EFC Status

```{r chunk95625462} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Zero EFC Status

```{r chunk28502858} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Pell Recipient Status

```{r chunk1562748} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Pell Recipient Status

```{r chunk57190618} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Parents' Highest Education Level

```{r chunk3130161} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Parents' Highest Education Level

```{r chunk91792823} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Race/Ethnicity

```{r chunk45395979} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Race/Ethnicity

```{r chunk86097948} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Institution HBCU Status

```{r chunk38798080} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Institution HBCU Status

```{r chunk667149} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Institution MSI Status

```{r chunk33024058} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Institution MSI Status

```{r chunk76155502} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Institution Selectivity

```{r chunk25065874} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Institution Selectivity

```{r chunk8107915} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Institution State

```{r chunk41932139} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Institution State

```{r chunk20163395} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### State grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving State grants by Income Quartile

```{r chunk37746436} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Income Quartile

```{r chunk18148946} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving State grants by Zero EFC Status

```{r chunk52757386} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Zero EFC Status

```{r chunk51716600} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving State grants by Pell Recipient Status

```{r chunk26382799} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Pell Recipient Status

```{r chunk34268056} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving State grants by Parents' Highest Education Level

```{r chunk38139688} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Parents' Highest Education Level

```{r chunk45274648} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving State grants by Race/Ethnicity

```{r chunk66854634} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Race/Ethnicity

```{r chunk85793417} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving State grants by Institution HBCU Status

```{r chunk43319984} 
chartFn1(targetName="State grants total", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Institution HBCU Status

```{r chunk13711651} 
chartFn1(targetName="State grants total", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving State grants by Institution MSI Status

```{r chunk15912974} 
chartFn1(targetName="State grants total", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Institution MSI Status

```{r chunk89873235} 
chartFn1(targetName="State grants total", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving State grants by Institution Selectivity

```{r chunk68352228} 
chartFn1(targetName="State grants total", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Institution Selectivity

```{r chunk49461011} 
chartFn1(targetName="State grants total", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving State grants by Institution State

```{r chunk42285751} 
chartFn1(targetName="State grants total", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Institution State

```{r chunk34117215} 
chartFn1(targetName="State grants total", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Institution grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving Institution grants by Income Quartile

```{r chunk67473951} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Income Quartile

```{r chunk49672332} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Institution grants by Zero EFC Status

```{r chunk3228115} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Zero EFC Status

```{r chunk16823944} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Institution grants by Pell Recipient Status

```{r chunk31585463} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Pell Recipient Status

```{r chunk82177570} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Institution grants by Parents' Highest Education Level

```{r chunk94118198} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Parents' Highest Education Level

```{r chunk64583194} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Institution grants by Race/Ethnicity

```{r chunk12853002} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Race/Ethnicity

```{r chunk96324196} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Institution grants by Institution HBCU Status

```{r chunk18964806} 
chartFn1(targetName="Institution grants total", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Institution HBCU Status

```{r chunk59592458} 
chartFn1(targetName="Institution grants total", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Institution grants by Institution MSI Status

```{r chunk25846020} 
chartFn1(targetName="Institution grants total", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Institution MSI Status

```{r chunk27276977} 
chartFn1(targetName="Institution grants total", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Institution grants by Institution Selectivity

```{r chunk35134043} 
chartFn1(targetName="Institution grants total", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Institution Selectivity

```{r chunk62172712} 
chartFn1(targetName="Institution grants total", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Institution grants by Institution State

```{r chunk89569622} 
chartFn1(targetName="Institution grants total", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Institution State

```{r chunk36662164} 
chartFn1(targetName="Institution grants total", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Private source grants

####  {.tabset}

##### By Income Quartile

###### Share receiving Private source grants by Income Quartile

```{r chunk17841061} 
chartFn1(targetName="Private source grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Income Quartile

```{r chunk41052147} 
chartFn1(targetName="Private source grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Private source grants by Zero EFC Status

```{r chunk86310074} 
chartFn1(targetName="Private source grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Zero EFC Status

```{r chunk22267886} 
chartFn1(targetName="Private source grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Private source grants by Pell Recipient Status

```{r chunk17416769} 
chartFn1(targetName="Private source grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Pell Recipient Status

```{r chunk93186622} 
chartFn1(targetName="Private source grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Private source grants by Parents' Highest Education Level

```{r chunk88985257} 
chartFn1(targetName="Private source grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Parents' Highest Education Level

```{r chunk59745086} 
chartFn1(targetName="Private source grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Private source grants by Race/Ethnicity

```{r chunk77081415} 
chartFn1(targetName="Private source grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Race/Ethnicity

```{r chunk28375590} 
chartFn1(targetName="Private source grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Private source grants by Institution HBCU Status

```{r chunk22343539} 
chartFn1(targetName="Private source grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Institution HBCU Status

```{r chunk38169253} 
chartFn1(targetName="Private source grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Private source grants by Institution MSI Status

```{r chunk66724763} 
chartFn1(targetName="Private source grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Institution MSI Status

```{r chunk63480929} 
chartFn1(targetName="Private source grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Private source grants by Institution Selectivity

```{r chunk73482603} 
chartFn1(targetName="Private source grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Institution Selectivity

```{r chunk40719902} 
chartFn1(targetName="Private source grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Private source grants by Institution State

```{r chunk48409796} 
chartFn1(targetName="Private source grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Institution State

```{r chunk77279733} 
chartFn1(targetName="Private source grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

## Unit A2: Need-based and non-need-based aid 

### State non-need & merit grants

####  {.tabset}

##### By Income Quartile

###### Share receiving State non-need & merit grants by Income Quartile

```{r chunk147889} 
chartFn1(targetName="State non-need & merit grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Income Quartile

```{r chunk74588068} 
chartFn1(targetName="State non-need & merit grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving State non-need & merit grants by Zero EFC Status

```{r chunk55535111} 
chartFn1(targetName="State non-need & merit grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Zero EFC Status

```{r chunk42878383} 
chartFn1(targetName="State non-need & merit grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving State non-need & merit grants by Pell Recipient Status

```{r chunk56195529} 
chartFn1(targetName="State non-need & merit grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Pell Recipient Status

```{r chunk80217125} 
chartFn1(targetName="State non-need & merit grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving State non-need & merit grants by Parents' Highest Education Level

```{r chunk66095679} 
chartFn1(targetName="State non-need & merit grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Parents' Highest Education Level

```{r chunk71072449} 
chartFn1(targetName="State non-need & merit grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving State non-need & merit grants by Race/Ethnicity

```{r chunk38448956} 
chartFn1(targetName="State non-need & merit grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Race/Ethnicity

```{r chunk82122295} 
chartFn1(targetName="State non-need & merit grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving State non-need & merit grants by Institution HBCU Status

```{r chunk23400099} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Institution HBCU Status

```{r chunk59144586} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving State non-need & merit grants by Institution MSI Status

```{r chunk19870264} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Institution MSI Status

```{r chunk32515965} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving State non-need & merit grants by Institution Selectivity

```{r chunk45839754} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Institution Selectivity

```{r chunk3717282} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving State non-need & merit grants by Institution State

```{r chunk4369137} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Institution State

```{r chunk42746161} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-} 
 
### State need-based grants

####  {.tabset}

##### By Income Quartile

###### Share receiving State need-based grants by Income Quartile

```{r chunk77466168} 
chartFn1(targetName="State need-based grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Income Quartile

```{r chunk15723440} 
chartFn1(targetName="State need-based grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving State need-based grants by Zero EFC Status

```{r chunk17426853} 
chartFn1(targetName="State need-based grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Zero EFC Status

```{r chunk65418731} 
chartFn1(targetName="State need-based grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving State need-based grants by Pell Recipient Status

```{r chunk83972761} 
chartFn1(targetName="State need-based grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Pell Recipient Status

```{r chunk56048092} 
chartFn1(targetName="State need-based grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving State need-based grants by Parents' Highest Education Level

```{r chunk23658913} 
chartFn1(targetName="State need-based grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Parents' Highest Education Level

```{r chunk89609677} 
chartFn1(targetName="State need-based grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving State need-based grants by Race/Ethnicity

```{r chunk90309778} 
chartFn1(targetName="State need-based grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Race/Ethnicity

```{r chunk4982586} 
chartFn1(targetName="State need-based grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving State need-based grants by Institution HBCU Status

```{r chunk21513456} 
chartFn1(targetName="State need-based grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Institution HBCU Status

```{r chunk50992486} 
chartFn1(targetName="State need-based grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving State need-based grants by Institution MSI Status

```{r chunk3932634} 
chartFn1(targetName="State need-based grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Institution MSI Status

```{r chunk66138616} 
chartFn1(targetName="State need-based grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving State need-based grants by Institution Selectivity

```{r chunk62022458} 
chartFn1(targetName="State need-based grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Institution Selectivity

```{r chunk96925196} 
chartFn1(targetName="State need-based grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving State need-based grants by Institution State

```{r chunk85373274} 
chartFn1(targetName="State need-based grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Institution State

```{r chunk63215453} 
chartFn1(targetName="State need-based grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Institution non-need & merit grants

####  {.tabset}

##### By Income Quartile

###### Share receiving Institution non-need & merit grants by Income Quartile

```{r chunk51644472} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Income Quartile

```{r chunk81590431} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Institution non-need & merit grants by Zero EFC Status

```{r chunk92593062} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Zero EFC Status

```{r chunk40351818} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Institution non-need & merit grants by Pell Recipient Status

```{r chunk7224502} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Pell Recipient Status

```{r chunk56816818} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Institution non-need & merit grants by Parents' Highest Education Level

```{r chunk65728367} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Parents' Highest Education Level

```{r chunk88066992} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Institution non-need & merit grants by Race/Ethnicity

```{r chunk763527} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Race/Ethnicity

```{r chunk51908940} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Institution non-need & merit grants by Institution HBCU Status

```{r chunk85613214} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Institution HBCU Status

```{r chunk62921908} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Institution non-need & merit grants by Institution MSI Status

```{r chunk23737518} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Institution MSI Status

```{r chunk16976093} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Institution non-need & merit grants by Institution Selectivity

```{r chunk74171048} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Institution Selectivity

```{r chunk49127127} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Institution non-need & merit grants by Institution State

```{r chunk84624721} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Institution State

```{r chunk49784115} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Institutional need-based grants

####  {.tabset}

##### By Income Quartile

###### Share receiving Institutional need-based grants by Income Quartile

```{r chunk2694975} 
chartFn1(targetName="Institutional need-based grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Income Quartile

```{r chunk79361602} 
chartFn1(targetName="Institutional need-based grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Institutional need-based grants by Zero EFC Status

```{r chunk24380978} 
chartFn1(targetName="Institutional need-based grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Zero EFC Status

```{r chunk81976761} 
chartFn1(targetName="Institutional need-based grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Institutional need-based grants by Pell Recipient Status

```{r chunk24525782} 
chartFn1(targetName="Institutional need-based grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Pell Recipient Status

```{r chunk25362643} 
chartFn1(targetName="Institutional need-based grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Institutional need-based grants by Parents' Highest Education Level

```{r chunk547868} 
chartFn1(targetName="Institutional need-based grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Parents' Highest Education Level

```{r chunk68315542} 
chartFn1(targetName="Institutional need-based grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Institutional need-based grants by Race/Ethnicity

```{r chunk45449622} 
chartFn1(targetName="Institutional need-based grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Race/Ethnicity

```{r chunk18965281} 
chartFn1(targetName="Institutional need-based grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Institutional need-based grants by Institution HBCU Status

```{r chunk71782320} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Institution HBCU Status

```{r chunk26692580} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Institutional need-based grants by Institution MSI Status

```{r chunk36050877} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Institution MSI Status

```{r chunk25682061} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Institutional need-based grants by Institution Selectivity

```{r chunk70246750} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Institution Selectivity

```{r chunk89168507} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Institutional need-based grants by Institution State

```{r chunk35178007} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Institution State

```{r chunk30129445} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

## Unit A3: Combined aid measures 

### Total state and institutional grants

####  {.tabset}

##### By Income Quartile

###### Share receiving state or institutional grants by Income Quartile

```{r chunk78734766} 
chartFn1(targetName="Total state and institutional grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Income Quartile

```{r chunk56685630} 
chartFn1(targetName="Total state and institutional grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving state or institutional grants by Zero EFC Status

```{r chunk80704094} 
chartFn1(targetName="Total state and institutional grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Zero EFC Status

```{r chunk94497578} 
chartFn1(targetName="Total state and institutional grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving state or institutional grants by Pell Recipient Status

```{r chunk80418791} 
chartFn1(targetName="Total state and institutional grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Pell Recipient Status

```{r chunk66498923} 
chartFn1(targetName="Total state and institutional grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving state or institutional grants by Parents' Highest Education Level

```{r chunk43990511} 
chartFn1(targetName="Total state and institutional grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Parents' Highest Education Level

```{r chunk87630790} 
chartFn1(targetName="Total state and institutional grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving state or institutional grants by Race/Ethnicity

```{r chunk97731556} 
chartFn1(targetName="Total state and institutional grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Race/Ethnicity

```{r chunk9416067} 
chartFn1(targetName="Total state and institutional grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving state or institutional grants by Institution HBCU Status

```{r chunk28009272} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Institution HBCU Status

```{r chunk39836673} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving state or institutional grants by Institution MSI Status

```{r chunk56741783} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Institution MSI Status

```{r chunk3710642} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving state or institutional grants by Institution Selectivity

```{r chunk56854978} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Institution Selectivity

```{r chunk53096604} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving state or institutional grants by Institution State

```{r chunk66889175} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Institution State

```{r chunk37552824} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Grant amount exceeding federal need

####  {.tabset}

##### By Income Quartile

###### Share whose grants exceed federal need by Income Quartile

```{r chunk323187} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Income Quartile

```{r chunk52589831} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share whose grants exceed federal need by Zero EFC Status

```{r chunk30058040} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Zero EFC Status

```{r chunk98041459} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share whose grants exceed federal need by Pell Recipient Status

```{r chunk40577623} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Pell Recipient Status

```{r chunk39333777} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share whose grants exceed federal need by Parents' Highest Education Level

```{r chunk23680361} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Parents' Highest Education Level

```{r chunk41888744} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share whose grants exceed federal need by Race/Ethnicity

```{r chunk21740877} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Race/Ethnicity

```{r chunk2832997} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share whose grants exceed federal need by Institution HBCU Status

```{r chunk9570250} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Institution HBCU Status

```{r chunk28327742} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share whose grants exceed federal need by Institution MSI Status

```{r chunk99025330} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Institution MSI Status

```{r chunk75660055} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share whose grants exceed federal need by Institution Selectivity

```{r chunk78590006} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Institution Selectivity

```{r chunk83746527} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share whose grants exceed federal need by Institution State

```{r chunk81635797} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Institution State

```{r chunk59717321} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

## Unit A4: Net price 

### Tuition and fees minus all grants

####  {.tabset}

##### By Income Quartile

###### Share with unmet tuition and fees after all grants by Income Quartile

```{r chunk30621285} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Income Quartile

```{r chunk88647911} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Income Quartile

```{r chunk38958751} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share with unmet tuition and fees after all grants by Zero EFC Status

```{r chunk4310080} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Zero EFC Status

```{r chunk20597620} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Zero EFC Status

```{r chunk39586079} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share with unmet tuition and fees after all grants by Pell Recipient Status

```{r chunk78130159} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Pell Recipient Status

```{r chunk45865292} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Pell Recipient Status

```{r chunk69839582} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share with unmet tuition and fees after all grants by Parents' Highest Education Level

```{r chunk8938016} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Parents' Highest Education Level

```{r chunk94571548} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Parents' Highest Education Level

```{r chunk78668323} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share with unmet tuition and fees after all grants by Race/Ethnicity

```{r chunk29988756} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Race/Ethnicity

```{r chunk31577731} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Race/Ethnicity

```{r chunk47284659} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share with unmet tuition and fees after all grants by Institution HBCU Status

```{r chunk77860182} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Institution HBCU Status

```{r chunk22197055} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Institution HBCU Status

```{r chunk47676141} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share with unmet tuition and fees after all grants by Institution MSI Status

```{r chunk39181036} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Institution MSI Status

```{r chunk71352407} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Institution MSI Status

```{r chunk9583780} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share with unmet tuition and fees after all grants by Institution Selectivity

```{r chunk28240668} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Institution Selectivity

```{r chunk98356470} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Institution Selectivity

```{r chunk91089236} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share with unmet tuition and fees after all grants by Institution State

```{r chunk71001855} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Institution State

```{r chunk9243579} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Institution State

```{r chunk62652923} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Net tuition after all grants as percent of income

####  {.tabset}

##### By Income Quartile

###### Median net tuition and fees after all grants as a percentage of income by Income Quartile

```{r chunk51626285} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median net tuition and fees after all grants as a percentage of income by Zero EFC Status

```{r chunk67481360} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median net tuition and fees after all grants as a percentage of income by Pell Recipient Status

```{r chunk41637712} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median net tuition and fees after all grants as a percentage of income by Parents' Highest Education Level

```{r chunk16570251} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median net tuition and fees after all grants as a percentage of income by Race/Ethnicity

```{r chunk23036083} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median net tuition and fees after all grants as a percentage of income by Institution HBCU Status

```{r chunk47649822} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Median net tuition and fees after all grants as a percentage of income by Institution MSI Status

```{r chunk13580993} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Median net tuition and fees after all grants as a percentage of income by Institution Selectivity

```{r chunk74075400} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median net tuition and fees after all grants as a percentage of income by Institution State

```{r chunk26625888} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Student budget minus all grants

####  {.tabset}

##### By Income Quartile

###### Average net student budget after all grants by Income Quartile

```{r chunk7072322} 
chartFn1(targetName="Student budget minus all grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Income Quartile

```{r chunk30090899} 
chartFn1(targetName="Student budget minus all grants", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Average net student budget after all grants by Zero EFC Status

```{r chunk92374924} 
chartFn1(targetName="Student budget minus all grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Zero EFC Status

```{r chunk5701617} 
chartFn1(targetName="Student budget minus all grants", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Average net student budget after all grants by Pell Recipient Status

```{r chunk81093029} 
chartFn1(targetName="Student budget minus all grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Pell Recipient Status

```{r chunk26365901} 
chartFn1(targetName="Student budget minus all grants", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Average net student budget after all grants by Parents' Highest Education Level

```{r chunk55900684} 
chartFn1(targetName="Student budget minus all grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Parents' Highest Education Level

```{r chunk2096444} 
chartFn1(targetName="Student budget minus all grants", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Average net student budget after all grants by Race/Ethnicity

```{r chunk12721994} 
chartFn1(targetName="Student budget minus all grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Race/Ethnicity

```{r chunk73716230} 
chartFn1(targetName="Student budget minus all grants", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Average net student budget after all grants by Institution HBCU Status

```{r chunk6648436} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Institution HBCU Status

```{r chunk24905843} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Average net student budget after all grants by Institution MSI Status

```{r chunk62139759} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Institution MSI Status

```{r chunk89582824} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Average net student budget after all grants by Institution Selectivity

```{r chunk66253929} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Institution Selectivity

```{r chunk17009305} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Average net student budget after all grants by Institution State

```{r chunk44753364} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Institution State

```{r chunk23874514} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Net price after grants as percent of income

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants as a percentage of income by Income Quartile

```{r chunk72072136} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median net student budget after all grants as a percentage of income by Zero EFC Status

```{r chunk8964842} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median net student budget after all grants as a percentage of income by Pell Recipient Status

```{r chunk21497503} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median net student budget after all grants as a percentage of income by Parents' Highest Education Level

```{r chunk84612892} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median net student budget after all grants as a percentage of income by Race/Ethnicity

```{r chunk82607451} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median net student budget after all grants as a percentage of income by Institution HBCU Status

```{r chunk4582512} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Median net student budget after all grants as a percentage of income by Institution MSI Status

```{r chunk16005624} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Median net student budget after all grants as a percentage of income by Institution Selectivity

```{r chunk77476082} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median net student budget after all grants as a percentage of income by Institution State

```{r chunk66410707} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

## Unit A5: Context 

### Expected Family Contribution

####  {.tabset}

##### By Income Quartile

###### Median Expected Family Contribution by Income Quartile

```{r chunk26529325} 
chartFn1(targetName="Expected Family Contribution", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median Expected Family Contribution by Zero EFC Status

```{r chunk55034380} 
chartFn1(targetName="Expected Family Contribution", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median Expected Family Contribution by Pell Recipient Status

```{r chunk14627895} 
chartFn1(targetName="Expected Family Contribution", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median Expected Family Contribution by Parents' Highest Education Level

```{r chunk80785932} 
chartFn1(targetName="Expected Family Contribution", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median Expected Family Contribution by Race/Ethnicity

```{r chunk127443} 
chartFn1(targetName="Expected Family Contribution", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median Expected Family Contribution by Institution HBCU Status

```{r chunk40513851} 
chartFn1(targetName="Expected Family Contribution", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Median Expected Family Contribution by Institution MSI Status

```{r chunk53877674} 
chartFn1(targetName="Expected Family Contribution", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Median Expected Family Contribution by Institution Selectivity

```{r chunk18454728} 
chartFn1(targetName="Expected Family Contribution", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median Expected Family Contribution by Institution State

```{r chunk79815942} 
chartFn1(targetName="Expected Family Contribution", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### High School GPA

####  {.tabset}

##### By Income Quartile

###### Distribution of High School GPA by Income Quartile

```{r chunk69111367} 
chartFn2(distributionName="High School GPA", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of High School GPA by Zero EFC Status

```{r chunk78838351} 
chartFn2(distributionName="High School GPA", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of High School GPA by Pell Recipient Status

```{r chunk4480418} 
chartFn2(distributionName="High School GPA", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of High School GPA by Parents' Highest Education Level

```{r chunk15614645} 
chartFn2(distributionName="High School GPA", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of High School GPA by Race/Ethnicity

```{r chunk23645188} 
chartFn2(distributionName="High School GPA", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of High School GPA by Institution HBCU Status

```{r chunk21585575} 
chartFn2(distributionName="High School GPA", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of High School GPA by Institution MSI Status

```{r chunk88406244} 
chartFn2(distributionName="High School GPA", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of High School GPA by Institution Selectivity

```{r chunk61918527} 
chartFn2(distributionName="High School GPA", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of High School GPA by Institution State

```{r chunk58769353} 
chartFn2(distributionName="High School GPA", rowName="Institution State")
```

#### {-}

### Tuition and fees paid

####  {.tabset}

##### By Income Quartile

###### Median tuition and fees paid by Income Quartile

```{r chunk57895933} 
chartFn1(targetName="Tuition and fees paid", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median tuition and fees paid by Zero EFC Status

```{r chunk38153193} 
chartFn1(targetName="Tuition and fees paid", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median tuition and fees paid by Pell Recipient Status

```{r chunk70198910} 
chartFn1(targetName="Tuition and fees paid", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median tuition and fees paid by Parents' Highest Education Level

```{r chunk48566414} 
chartFn1(targetName="Tuition and fees paid", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median tuition and fees paid by Race/Ethnicity

```{r chunk53374166} 
chartFn1(targetName="Tuition and fees paid", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median tuition and fees paid by Institution HBCU Status

```{r chunk44091555} 
chartFn1(targetName="Tuition and fees paid", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median tuition and fees paid by Institution State

```{r chunk77302470} 
chartFn1(targetName="Tuition and fees paid", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Student budget (attendance adjusted)

####  {.tabset}

##### By Income Quartile

###### Median student budget (attendance adjusted) by Income Quartile

```{r chunk82433907} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median student budget (attendance adjusted) by Zero EFC Status

```{r chunk77385065} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median student budget (attendance adjusted) by Pell Recipient Status

```{r chunk6279823} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median student budget (attendance adjusted) by Parents' Highest Education Level

```{r chunk45346010} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median student budget (attendance adjusted) by Race/Ethnicity

```{r chunk49422474} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median student budget (attendance adjusted) by Institution HBCU Status

```{r chunk98537518} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Median student budget (attendance adjusted) by Institution MSI Status

```{r chunk70474364} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Median student budget (attendance adjusted) by Institution Selectivity

```{r chunk71053720} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median student budget (attendance adjusted) by Institution State

```{r chunk14462049} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

# Section B: State public four-year sectors

## Unit B1: Distributions of aid programs

### State grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving State grants by Income Quartile

```{r chunk17568446} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Income Quartile

```{r chunk59735096} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Share receiving State grants by Zero EFC Status

```{r chunk89249568} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Zero EFC Status

```{r chunk64577192} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Share receiving State grants by Pell Recipient Status

```{r chunk80032095} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Pell Recipient Status

```{r chunk5125527} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Share receiving State grants by Parents' Highest Education Level

```{r chunk15023497} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Parents' Highest Education Level

```{r chunk96070968} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Share receiving State grants by Race/Ethnicity

```{r chunk16749953} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Race/Ethnicity

```{r chunk35949109} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

### Institution grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving Institution grants by Income Quartile

```{r chunk50745611} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Income Quartile

```{r chunk43216176} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Share receiving Institution grants by Zero EFC Status

```{r chunk3574275} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Zero EFC Status

```{r chunk43692847} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Share receiving Institution grants by Pell Recipient Status

```{r chunk37216563} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Pell Recipient Status

```{r chunk56041219} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Share receiving Institution grants by Parents' Highest Education Level

```{r chunk27815223} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Parents' Highest Education Level

```{r chunk36710235} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Share receiving Institution grants by Race/Ethnicity

```{r chunk8318392} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Race/Ethnicity

```{r chunk93558017} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

## Unit B2: Net price

### Student budget minus all grants

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants by Income Quartile

```{r chunk67220919} 
chartFn1(targetName="Student budget minus all grants", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Median net student budget after all grants by Zero EFC Status

```{r chunk90933196} 
chartFn1(targetName="Student budget minus all grants", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Median net student budget after all grants by Pell Recipient Status

```{r chunk5142312} 
chartFn1(targetName="Student budget minus all grants", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Median net student budget after all grants by Parents' Highest Education Level

```{r chunk57309913} 
chartFn1(targetName="Student budget minus all grants", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Median net student budget after all grants by Race/Ethnicity

```{r chunk95999672} 
chartFn1(targetName="Student budget minus all grants", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

### Net price after grants as percent of income

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants as a percentage of income by Income Quartile

```{r chunk77671417} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Median net student budget after all grants as a percentage of income by Zero EFC Status

```{r chunk40101387} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Median net student budget after all grants as a percentage of income by Pell Recipient Status

```{r chunk24887600} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Median net student budget after all grants as a percentage of income by Parents' Highest Education Level

```{r chunk9663917} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Median net student budget after all grants as a percentage of income by Race/Ethnicity

```{r chunk61505285} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

## Unit B3: Context

### Student budget (attendance adjusted)

####  {.tabset}

##### By Income Quartile

###### Median student budget (attendance adjusted) by Income Quartile

```{r chunk24593966} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Median student budget (attendance adjusted) by Zero EFC Status

```{r chunk35111846} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Median student budget (attendance adjusted) by Pell Recipient Status

```{r chunk98776166} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Median student budget (attendance adjusted) by Parents' Highest Education Level

```{r chunk6461224} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Median student budget (attendance adjusted) by Race/Ethnicity

```{r chunk56663130} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

# Section C: State public two-year sectors

## Unit C1: Distributions of aid programs

### State grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving State grants by Income Quartile

```{r chunk49571211} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Income Quartile

```{r chunk46240588} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Share receiving State grants by Zero EFC Status

```{r chunk52618371} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Zero EFC Status

```{r chunk52566867} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Share receiving State grants by Pell Recipient Status

```{r chunk29946108} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Pell Recipient Status

```{r chunk51567092} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Share receiving State grants by Parents' Highest Education Level

```{r chunk72062326} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Parents' Highest Education Level

```{r chunk40281} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Share receiving State grants by Race/Ethnicity

```{r chunk20996483} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Race/Ethnicity

```{r chunk72835120} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

### Institution grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving Institution grants by Income Quartile

```{r chunk90179463} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Income Quartile

```{r chunk31221467} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Share receiving Institution grants by Zero EFC Status

```{r chunk49250283} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Zero EFC Status

```{r chunk13852389} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Share receiving Institution grants by Pell Recipient Status

```{r chunk10271378} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Pell Recipient Status

```{r chunk13125137} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Share receiving Institution grants by Parents' Highest Education Level

```{r chunk38214239} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Parents' Highest Education Level

```{r chunk75445375} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Share receiving Institution grants by Race/Ethnicity

```{r chunk59264608} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Race/Ethnicity

```{r chunk35185685} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

## Unit C2: Net price

### Student budget minus all grants

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants by Income Quartile

```{r chunk18536958} 
chartFn1(targetName="Student budget minus all grants", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Median net student budget after all grants by Zero EFC Status

```{r chunk47333721} 
chartFn1(targetName="Student budget minus all grants", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Median net student budget after all grants by Pell Recipient Status

```{r chunk67817845} 
chartFn1(targetName="Student budget minus all grants", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Median net student budget after all grants by Parents' Highest Education Level

```{r chunk17492098} 
chartFn1(targetName="Student budget minus all grants", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Median net student budget after all grants by Race/Ethnicity

```{r chunk68366166} 
chartFn1(targetName="Student budget minus all grants", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

### Net price after grants as percent of income

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants as a percentage of income by Income Quartile

```{r chunk31999616} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Median net student budget after all grants as a percentage of income by Zero EFC Status

```{r chunk84794674} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Median net student budget after all grants as a percentage of income by Pell Recipient Status

```{r chunk49717969} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Median net student budget after all grants as a percentage of income by Parents' Highest Education Level

```{r chunk65967164} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Median net student budget after all grants as a percentage of income by Race/Ethnicity

```{r chunk80743284} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

## Unit C3: Context

####  {.tabset}

### Student budget (attendance adjusted)

##### By Income Quartile

###### Median student budget (attendance adjusted) by Income Quartile

```{r chunk79634960} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Median student budget (attendance adjusted) by Zero EFC Status

```{r chunk28112054} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Median student budget (attendance adjusted) by Pell Recipient Status

```{r chunk47516273} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Median student budget (attendance adjusted) by Parents' Highest Education Level

```{r chunk85050934} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Median student budget (attendance adjusted) by Race/Ethnicity

```{r chunk47244698} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

# Section D: Distributions across variables 

## Unit D1: Distributions across variables 

### Income Quartile

####  {.tabset}

##### Overall

###### Distribution of Income Quartile

```{r chunk21285487} 
chartFn2(distributionName="Income Quartile", rowName="Overall")
```
 
##### By Zero EFC Status

###### Distribution of Income Quartile by Zero EFC Status

```{r chunk61110952} 
chartFn2(distributionName="Income Quartile", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Income Quartile by Pell Recipient Status

```{r chunk60880357} 
chartFn2(distributionName="Income Quartile", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Income Quartile by Parents' Highest Education Level

```{r chunk50159729} 
chartFn2(distributionName="Income Quartile", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Income Quartile by Race/Ethnicity

```{r chunk2673506} 
chartFn2(distributionName="Income Quartile", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Income Quartile by Institution HBCU Status

```{r chunk81535522} 
chartFn2(distributionName="Income Quartile", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Income Quartile by Institution MSI Status

```{r chunk97252930} 
chartFn2(distributionName="Income Quartile", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Income Quartile by Institution Selectivity

```{r chunk88980865} 
chartFn2(distributionName="Income Quartile", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Income Quartile by Institution State

```{r chunk76352259} 
chartFn2(distributionName="Income Quartile", rowName="Institution State")
```

#### {-}

### Zero EFC Status

####  {.tabset}

##### Overall

###### Distribution of Zero EFC Status

```{r chunk52557812} 
chartFn2(distributionName="Zero EFC Status", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Zero EFC Status by Income Quartile

```{r chunk62877694} 
chartFn2(distributionName="Zero EFC Status", rowName="Income Quartile")
```
 
##### By Pell Recipient Status

###### Distribution of Zero EFC Status by Pell Recipient Status

```{r chunk22397449} 
chartFn2(distributionName="Zero EFC Status", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Zero EFC Status by Parents' Highest Education Level

```{r chunk1739577} 
chartFn2(distributionName="Zero EFC Status", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Zero EFC Status by Race/Ethnicity

```{r chunk93806167} 
chartFn2(distributionName="Zero EFC Status", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Zero EFC Status by Institution HBCU Status

```{r chunk60057384} 
chartFn2(distributionName="Zero EFC Status", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Zero EFC Status by Institution MSI Status

```{r chunk13462969} 
chartFn2(distributionName="Zero EFC Status", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Zero EFC Status by Institution Selectivity

```{r chunk21818645} 
chartFn2(distributionName="Zero EFC Status", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Zero EFC Status by Institution State

```{r chunk66404237} 
chartFn2(distributionName="Zero EFC Status", rowName="Institution State")
```

#### {-}

### Pell Recipient Status

####  {.tabset}

##### Overall

###### Distribution of Pell Recipient Status

```{r chunk50423723} 
chartFn2(distributionName="Pell Recipient Status", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Pell Recipient Status by Income Quartile

```{r chunk10341132} 
chartFn2(distributionName="Pell Recipient Status", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Pell Recipient Status by Zero EFC Status

```{r chunk87337223} 
chartFn2(distributionName="Pell Recipient Status", rowName="Zero EFC Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Pell Recipient Status by Parents' Highest Education Level

```{r chunk20513581} 
chartFn2(distributionName="Pell Recipient Status", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Pell Recipient Status by Race/Ethnicity

```{r chunk21042589} 
chartFn2(distributionName="Pell Recipient Status", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Pell Recipient Status by Institution HBCU Status

```{r chunk8637916} 
chartFn2(distributionName="Pell Recipient Status", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Pell Recipient Status by Institution MSI Status

```{r chunk34446016} 
chartFn2(distributionName="Pell Recipient Status", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Pell Recipient Status by Institution Selectivity

```{r chunk93142296} 
chartFn2(distributionName="Pell Recipient Status", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Pell Recipient Status by Institution State

```{r chunk53915545} 
chartFn2(distributionName="Pell Recipient Status", rowName="Institution State")
```

#### {-}

### Parents' Highest Education Level

####  {.tabset}

##### Overall

###### Distribution of Parents' Highest Education Level

```{r chunk50981952} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Parents' Highest Education Level by Income Quartile

```{r chunk10634790} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Parents' Highest Education Level by Zero EFC Status

```{r chunk7337061} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Parents' Highest Education Level by Pell Recipient Status

```{r chunk83980521} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Pell Recipient Status")
```
 
##### By Race/Ethnicity

###### Distribution of Parents' Highest Education Level by Race/Ethnicity

```{r chunk20888415} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Parents' Highest Education Level by Institution HBCU Status

```{r chunk11742342} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Parents' Highest Education Level by Institution MSI Status

```{r chunk449097} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Parents' Highest Education Level by Institution Selectivity

```{r chunk55869199} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Parents' Highest Education Level by Institution State

```{r chunk40402759} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Institution State")
```

#### {-}

### Race/Ethnicity

####  {.tabset}

##### Overall

###### Distribution of Race/Ethnicity

```{r chunk83424412} 
chartFn2(distributionName="Race/Ethnicity", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Race/Ethnicity by Income Quartile

```{r chunk97835230} 
chartFn2(distributionName="Race/Ethnicity", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Race/Ethnicity by Zero EFC Status

```{r chunk43878198} 
chartFn2(distributionName="Race/Ethnicity", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Race/Ethnicity by Pell Recipient Status

```{r chunk62457188} 
chartFn2(distributionName="Race/Ethnicity", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Race/Ethnicity by Parents' Highest Education Level

```{r chunk37090882} 
chartFn2(distributionName="Race/Ethnicity", rowName="Parents' Highest Education Level")
```
 
##### By Institution HBCU Status

###### Distribution of Race/Ethnicity by Institution HBCU Status

```{r chunk5361692} 
chartFn2(distributionName="Race/Ethnicity", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Race/Ethnicity by Institution MSI Status

```{r chunk78950206} 
chartFn2(distributionName="Race/Ethnicity", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Race/Ethnicity by Institution Selectivity

```{r chunk36318482} 
chartFn2(distributionName="Race/Ethnicity", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Race/Ethnicity by Institution State

```{r chunk5826190} 
chartFn2(distributionName="Race/Ethnicity", rowName="Institution State")
```

#### {-}

### Institution HBCU Status

####  {.tabset}

##### Overall

###### Distribution of Institution HBCU Status

```{r chunk56654027} 
chartFn2(distributionName="Institution HBCU Status", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Institution HBCU Status by Income Quartile

```{r chunk62720479} 
chartFn2(distributionName="Institution HBCU Status", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Institution HBCU Status by Zero EFC Status

```{r chunk76775898} 
chartFn2(distributionName="Institution HBCU Status", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Institution HBCU Status by Pell Recipient Status

```{r chunk34456158} 
chartFn2(distributionName="Institution HBCU Status", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Institution HBCU Status by Parents' Highest Education Level

```{r chunk4705165} 
chartFn2(distributionName="Institution HBCU Status", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Institution HBCU Status by Race/Ethnicity

```{r chunk81936383} 
chartFn2(distributionName="Institution HBCU Status", rowName="Race/Ethnicity")
```
 
##### By Institution MSI Status

###### Distribution of Institution HBCU Status by Institution MSI Status

```{r chunk96629739} 
chartFn2(distributionName="Institution HBCU Status", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Institution HBCU Status by Institution Selectivity

```{r chunk57559333} 
chartFn2(distributionName="Institution HBCU Status", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Institution HBCU Status by Institution State

```{r chunk2439493} 
chartFn2(distributionName="Institution HBCU Status", rowName="Institution State")
```

#### {-}

### Institution MSI Status

####  {.tabset}

##### Overall

###### Distribution of Institution MSI Status

```{r chunk41735544} 
chartFn2(distributionName="Institution MSI Status", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Institution MSI Status by Income Quartile

```{r chunk24690406} 
chartFn2(distributionName="Institution MSI Status", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Institution MSI Status by Zero EFC Status

```{r chunk36081062} 
chartFn2(distributionName="Institution MSI Status", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Institution MSI Status by Pell Recipient Status

```{r chunk90438112} 
chartFn2(distributionName="Institution MSI Status", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Institution MSI Status by Parents' Highest Education Level

```{r chunk62713825} 
chartFn2(distributionName="Institution MSI Status", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Institution MSI Status by Race/Ethnicity

```{r chunk57783129} 
chartFn2(distributionName="Institution MSI Status", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Institution MSI Status by Institution HBCU Status

```{r chunk20928641} 
chartFn2(distributionName="Institution MSI Status", rowName="Institution HBCU Status")
```
 
##### By Institution Selectivity

###### Distribution of Institution MSI Status by Institution Selectivity

```{r chunk37268494} 
chartFn2(distributionName="Institution MSI Status", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Institution MSI Status by Institution State

```{r chunk35218199} 
chartFn2(distributionName="Institution MSI Status", rowName="Institution State")
```

#### {-}

### Institution Selectivity

####  {.tabset}

##### Overall

###### Distribution of Institution Selectivity

```{r chunk86891062} 
chartFn2(distributionName="Institution Selectivity", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Institution Selectivity by Income Quartile

```{r chunk24159689} 
chartFn2(distributionName="Institution Selectivity", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Institution Selectivity by Zero EFC Status

```{r chunk71251531} 
chartFn2(distributionName="Institution Selectivity", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Institution Selectivity by Pell Recipient Status

```{r chunk76016375} 
chartFn2(distributionName="Institution Selectivity", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Institution Selectivity by Parents' Highest Education Level

```{r chunk21428687} 
chartFn2(distributionName="Institution Selectivity", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Institution Selectivity by Race/Ethnicity

```{r chunk51678473} 
chartFn2(distributionName="Institution Selectivity", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Institution Selectivity by Institution HBCU Status

```{r chunk41283899} 
chartFn2(distributionName="Institution Selectivity", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Institution Selectivity by Institution MSI Status

```{r chunk65594084} 
chartFn2(distributionName="Institution Selectivity", rowName="Institution MSI Status")
```
 
##### By Institution State

###### Distribution of Institution Selectivity by Institution State

```{r chunk60829118} 
chartFn2(distributionName="Institution Selectivity", rowName="Institution State")
```

#### {-}


