---
title: "Financial Aid Distributions"
author: "Peter Granville"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    toc: true
    toc_float: true
  
---

```{r setDefault, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r setup, include=FALSE}

```


Hey, you! Use the table of contents liberally! 

# Section A: Nationwide distributions of financial aid 

## Unit A1: Distributions of aid programs 

### Federal Pell Grant

####  {.tabset}

##### By Income Quartile

###### Share receiving Federal Pell Grant by Income Quartile

```{r chunk51901809} 
chartFn1(targetName="Federal Pell Grant", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Income Quartile

```{r chunk34608388} 
chartFn1(targetName="Federal Pell Grant", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Federal Pell Grant by Zero EFC Status

```{r chunk12999968} 
chartFn1(targetName="Federal Pell Grant", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Zero EFC Status

```{r chunk50201470} 
chartFn1(targetName="Federal Pell Grant", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Federal Pell Grant by Pell Recipient Status

```{r chunk49240993} 
chartFn1(targetName="Federal Pell Grant", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Pell Recipient Status

```{r chunk87506682} 
chartFn1(targetName="Federal Pell Grant", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Federal Pell Grant by Parents' Highest Education Level

```{r chunk62476864} 
chartFn1(targetName="Federal Pell Grant", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Parents' Highest Education Level

```{r chunk28274931} 
chartFn1(targetName="Federal Pell Grant", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Federal Pell Grant by Race/Ethnicity

```{r chunk99839860} 
chartFn1(targetName="Federal Pell Grant", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Race/Ethnicity

```{r chunk48558864} 
chartFn1(targetName="Federal Pell Grant", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Federal Pell Grant by Institution HBCU Status

```{r chunk3722066} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Institution HBCU Status

```{r chunk70893955} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Federal Pell Grant by Institution MSI Status

```{r chunk4947001} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Institution MSI Status

```{r chunk50988928} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Federal Pell Grant by Institution Selectivity

```{r chunk10588420} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Institution Selectivity

```{r chunk84453019} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Federal Pell Grant by Institution State

```{r chunk92018076} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal Pell Grant award by Institution State

```{r chunk93225442} 
chartFn1(targetName="Federal Pell Grant", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}
 
### Federal campus-based aid (SEOG, FWS)

####  {.tabset}

##### By Income Quartile

###### Share receiving Federal campus-based aid (SEOG, FWS) by Income Quartile

```{r chunk80796992} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Income Quartile

```{r chunk66753992} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Federal campus-based aid (SEOG, FWS) by Zero EFC Status

```{r chunk13320962} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Zero EFC Status

```{r chunk25654771} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Federal campus-based aid (SEOG, FWS) by Pell Recipient Status

```{r chunk17952826} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Pell Recipient Status

```{r chunk34566211} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Federal campus-based aid (SEOG, FWS) by Parents' Highest Education Level

```{r chunk15899056} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Parents' Highest Education Level

```{r chunk8396142} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Federal campus-based aid (SEOG, FWS) by Race/Ethnicity

```{r chunk67107596} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Race/Ethnicity

```{r chunk18498755} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Federal campus-based aid (SEOG, FWS) by Institution HBCU Status

```{r chunk81745155} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Institution HBCU Status

```{r chunk44965299} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Federal campus-based aid (SEOG, FWS) by Institution MSI Status

```{r chunk45950525} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Institution MSI Status

```{r chunk79514429} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Federal campus-based aid (SEOG, FWS) by Institution Selectivity

```{r chunk55571663} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Institution Selectivity

```{r chunk43163601} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Federal campus-based aid (SEOG, FWS) by Institution State

```{r chunk27577672} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Federal campus-based aid (SEOG, FWS) award by Institution State

```{r chunk25350575} 
chartFn1(targetName="Federal campus-based aid (SEOG, FWS)", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Title IV loans (includes Parent PLUS Loans)

####  {.tabset}

##### By Income Quartile

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Income Quartile

```{r chunk56592274} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Income Quartile

```{r chunk43183158} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Zero EFC Status

```{r chunk95625462} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Zero EFC Status

```{r chunk28502858} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Pell Recipient Status

```{r chunk1562748} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Pell Recipient Status

```{r chunk57190618} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Parents' Highest Education Level

```{r chunk3130161} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Parents' Highest Education Level

```{r chunk91792823} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Race/Ethnicity

```{r chunk45395979} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Race/Ethnicity

```{r chunk86097948} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Institution HBCU Status

```{r chunk38798080} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Institution HBCU Status

```{r chunk667149} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Institution MSI Status

```{r chunk33024058} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Institution MSI Status

```{r chunk76155502} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Institution Selectivity

```{r chunk25065874} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Institution Selectivity

```{r chunk8107915} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Title IV loans (includes Parent PLUS Loans) by Institution State

```{r chunk41932139} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Title IV loan (includes Parent PLUS Loans) amount by Institution State

```{r chunk20163395} 
chartFn1(targetName="Title IV loans (includes Parent PLUS Loans)", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### State grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving State grants by Income Quartile

```{r chunk37746436} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Income Quartile

```{r chunk18148946} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving State grants by Zero EFC Status

```{r chunk52757386} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Zero EFC Status

```{r chunk51716600} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving State grants by Pell Recipient Status

```{r chunk26382799} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Pell Recipient Status

```{r chunk34268056} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving State grants by Parents' Highest Education Level

```{r chunk38139688} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Parents' Highest Education Level

```{r chunk45274648} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving State grants by Race/Ethnicity

```{r chunk66854634} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Race/Ethnicity

```{r chunk85793417} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving State grants by Institution HBCU Status

```{r chunk43319984} 
chartFn1(targetName="State grants total", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Institution HBCU Status

```{r chunk13711651} 
chartFn1(targetName="State grants total", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving State grants by Institution MSI Status

```{r chunk15912974} 
chartFn1(targetName="State grants total", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Institution MSI Status

```{r chunk89873235} 
chartFn1(targetName="State grants total", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving State grants by Institution Selectivity

```{r chunk68352228} 
chartFn1(targetName="State grants total", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Institution Selectivity

```{r chunk49461011} 
chartFn1(targetName="State grants total", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving State grants by Institution State

```{r chunk42285751} 
chartFn1(targetName="State grants total", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State grant award by Institution State

```{r chunk34117215} 
chartFn1(targetName="State grants total", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Institution grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving Institution grants by Income Quartile

```{r chunk67473951} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Income Quartile

```{r chunk49672332} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Institution grants by Zero EFC Status

```{r chunk3228115} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Zero EFC Status

```{r chunk16823944} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Institution grants by Pell Recipient Status

```{r chunk31585463} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Pell Recipient Status

```{r chunk82177570} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Institution grants by Parents' Highest Education Level

```{r chunk94118198} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Parents' Highest Education Level

```{r chunk64583194} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Institution grants by Race/Ethnicity

```{r chunk12853002} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Race/Ethnicity

```{r chunk96324196} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Institution grants by Institution HBCU Status

```{r chunk18964806} 
chartFn1(targetName="Institution grants total", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Institution HBCU Status

```{r chunk59592458} 
chartFn1(targetName="Institution grants total", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Institution grants by Institution MSI Status

```{r chunk25846020} 
chartFn1(targetName="Institution grants total", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Institution MSI Status

```{r chunk27276977} 
chartFn1(targetName="Institution grants total", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Institution grants by Institution Selectivity

```{r chunk35134043} 
chartFn1(targetName="Institution grants total", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Institution Selectivity

```{r chunk62172712} 
chartFn1(targetName="Institution grants total", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Institution grants by Institution State

```{r chunk89569622} 
chartFn1(targetName="Institution grants total", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution grant award by Institution State

```{r chunk36662164} 
chartFn1(targetName="Institution grants total", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Private source grants

####  {.tabset}

##### By Income Quartile

###### Share receiving Private source grants by Income Quartile

```{r chunk17841061} 
chartFn1(targetName="Private source grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Income Quartile

```{r chunk41052147} 
chartFn1(targetName="Private source grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Private source grants by Zero EFC Status

```{r chunk86310074} 
chartFn1(targetName="Private source grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Zero EFC Status

```{r chunk22267886} 
chartFn1(targetName="Private source grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Private source grants by Pell Recipient Status

```{r chunk17416769} 
chartFn1(targetName="Private source grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Pell Recipient Status

```{r chunk93186622} 
chartFn1(targetName="Private source grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Private source grants by Parents' Highest Education Level

```{r chunk88985257} 
chartFn1(targetName="Private source grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Parents' Highest Education Level

```{r chunk59745086} 
chartFn1(targetName="Private source grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Private source grants by Race/Ethnicity

```{r chunk77081415} 
chartFn1(targetName="Private source grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Race/Ethnicity

```{r chunk28375590} 
chartFn1(targetName="Private source grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Private source grants by Institution HBCU Status

```{r chunk22343539} 
chartFn1(targetName="Private source grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Institution HBCU Status

```{r chunk38169253} 
chartFn1(targetName="Private source grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Private source grants by Institution MSI Status

```{r chunk66724763} 
chartFn1(targetName="Private source grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Institution MSI Status

```{r chunk63480929} 
chartFn1(targetName="Private source grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Private source grants by Institution Selectivity

```{r chunk73482603} 
chartFn1(targetName="Private source grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Institution Selectivity

```{r chunk40719902} 
chartFn1(targetName="Private source grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Private source grants by Institution State

```{r chunk48409796} 
chartFn1(targetName="Private source grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Private source grant award by Institution State

```{r chunk77279733} 
chartFn1(targetName="Private source grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

## Unit A2: Need-based and non-need-based aid 

### State non-need & merit grants

####  {.tabset}

##### By Income Quartile

###### Share receiving State non-need & merit grants by Income Quartile

```{r chunk147889} 
chartFn1(targetName="State non-need & merit grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Income Quartile

```{r chunk74588068} 
chartFn1(targetName="State non-need & merit grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving State non-need & merit grants by Zero EFC Status

```{r chunk55535111} 
chartFn1(targetName="State non-need & merit grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Zero EFC Status

```{r chunk42878383} 
chartFn1(targetName="State non-need & merit grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving State non-need & merit grants by Pell Recipient Status

```{r chunk56195529} 
chartFn1(targetName="State non-need & merit grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Pell Recipient Status

```{r chunk80217125} 
chartFn1(targetName="State non-need & merit grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving State non-need & merit grants by Parents' Highest Education Level

```{r chunk66095679} 
chartFn1(targetName="State non-need & merit grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Parents' Highest Education Level

```{r chunk71072449} 
chartFn1(targetName="State non-need & merit grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving State non-need & merit grants by Race/Ethnicity

```{r chunk38448956} 
chartFn1(targetName="State non-need & merit grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Race/Ethnicity

```{r chunk82122295} 
chartFn1(targetName="State non-need & merit grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving State non-need & merit grants by Institution HBCU Status

```{r chunk23400099} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Institution HBCU Status

```{r chunk59144586} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving State non-need & merit grants by Institution MSI Status

```{r chunk19870264} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Institution MSI Status

```{r chunk32515965} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving State non-need & merit grants by Institution Selectivity

```{r chunk45839754} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Institution Selectivity

```{r chunk3717282} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving State non-need & merit grants by Institution State

```{r chunk4369137} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State non-need & merit grant award by Institution State

```{r chunk42746161} 
chartFn1(targetName="State non-need & merit grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-} 
 
### State need-based grants

####  {.tabset}

##### By Income Quartile

###### Share receiving State need-based grants by Income Quartile

```{r chunk77466168} 
chartFn1(targetName="State need-based grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Income Quartile

```{r chunk15723440} 
chartFn1(targetName="State need-based grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving State need-based grants by Zero EFC Status

```{r chunk17426853} 
chartFn1(targetName="State need-based grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Zero EFC Status

```{r chunk65418731} 
chartFn1(targetName="State need-based grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving State need-based grants by Pell Recipient Status

```{r chunk83972761} 
chartFn1(targetName="State need-based grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Pell Recipient Status

```{r chunk56048092} 
chartFn1(targetName="State need-based grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving State need-based grants by Parents' Highest Education Level

```{r chunk23658913} 
chartFn1(targetName="State need-based grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Parents' Highest Education Level

```{r chunk89609677} 
chartFn1(targetName="State need-based grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving State need-based grants by Race/Ethnicity

```{r chunk90309778} 
chartFn1(targetName="State need-based grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Race/Ethnicity

```{r chunk4982586} 
chartFn1(targetName="State need-based grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving State need-based grants by Institution HBCU Status

```{r chunk21513456} 
chartFn1(targetName="State need-based grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Institution HBCU Status

```{r chunk50992486} 
chartFn1(targetName="State need-based grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving State need-based grants by Institution MSI Status

```{r chunk3932634} 
chartFn1(targetName="State need-based grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Institution MSI Status

```{r chunk66138616} 
chartFn1(targetName="State need-based grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving State need-based grants by Institution Selectivity

```{r chunk62022458} 
chartFn1(targetName="State need-based grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Institution Selectivity

```{r chunk96925196} 
chartFn1(targetName="State need-based grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving State need-based grants by Institution State

```{r chunk85373274} 
chartFn1(targetName="State need-based grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average State need-based grant award by Institution State

```{r chunk63215453} 
chartFn1(targetName="State need-based grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Institution non-need & merit grants

####  {.tabset}

##### By Income Quartile

###### Share receiving Institution non-need & merit grants by Income Quartile

```{r chunk51644472} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Income Quartile

```{r chunk81590431} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Institution non-need & merit grants by Zero EFC Status

```{r chunk92593062} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Zero EFC Status

```{r chunk40351818} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Institution non-need & merit grants by Pell Recipient Status

```{r chunk7224502} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Pell Recipient Status

```{r chunk56816818} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Institution non-need & merit grants by Parents' Highest Education Level

```{r chunk65728367} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Parents' Highest Education Level

```{r chunk88066992} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Institution non-need & merit grants by Race/Ethnicity

```{r chunk763527} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Race/Ethnicity

```{r chunk51908940} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Institution non-need & merit grants by Institution HBCU Status

```{r chunk85613214} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Institution HBCU Status

```{r chunk62921908} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Institution non-need & merit grants by Institution MSI Status

```{r chunk23737518} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Institution MSI Status

```{r chunk16976093} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Institution non-need & merit grants by Institution Selectivity

```{r chunk74171048} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Institution Selectivity

```{r chunk49127127} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Institution non-need & merit grants by Institution State

```{r chunk84624721} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institution non-need & merit grant award by Institution State

```{r chunk49784115} 
chartFn1(targetName="Institution non-need & merit grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Institutional need-based grants

####  {.tabset}

##### By Income Quartile

###### Share receiving Institutional need-based grants by Income Quartile

```{r chunk2694975} 
chartFn1(targetName="Institutional need-based grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Income Quartile

```{r chunk79361602} 
chartFn1(targetName="Institutional need-based grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving Institutional need-based grants by Zero EFC Status

```{r chunk24380978} 
chartFn1(targetName="Institutional need-based grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Zero EFC Status

```{r chunk81976761} 
chartFn1(targetName="Institutional need-based grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving Institutional need-based grants by Pell Recipient Status

```{r chunk24525782} 
chartFn1(targetName="Institutional need-based grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Pell Recipient Status

```{r chunk25362643} 
chartFn1(targetName="Institutional need-based grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving Institutional need-based grants by Parents' Highest Education Level

```{r chunk547868} 
chartFn1(targetName="Institutional need-based grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Parents' Highest Education Level

```{r chunk68315542} 
chartFn1(targetName="Institutional need-based grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving Institutional need-based grants by Race/Ethnicity

```{r chunk45449622} 
chartFn1(targetName="Institutional need-based grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Race/Ethnicity

```{r chunk18965281} 
chartFn1(targetName="Institutional need-based grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving Institutional need-based grants by Institution HBCU Status

```{r chunk71782320} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Institution HBCU Status

```{r chunk26692580} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving Institutional need-based grants by Institution MSI Status

```{r chunk36050877} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Institution MSI Status

```{r chunk25682061} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving Institutional need-based grants by Institution Selectivity

```{r chunk70246750} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Institution Selectivity

```{r chunk89168507} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving Institutional need-based grants by Institution State

```{r chunk35178007} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average Institutional need-based grant award by Institution State

```{r chunk30129445} 
chartFn1(targetName="Institutional need-based grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

## Unit A3: Combined aid measures 

### Total state and institutional grants

####  {.tabset}

##### By Income Quartile

###### Share receiving state or institutional grants by Income Quartile

```{r chunk78734766} 
chartFn1(targetName="Total state and institutional grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Income Quartile

```{r chunk56685630} 
chartFn1(targetName="Total state and institutional grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share receiving state or institutional grants by Zero EFC Status

```{r chunk80704094} 
chartFn1(targetName="Total state and institutional grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Zero EFC Status

```{r chunk94497578} 
chartFn1(targetName="Total state and institutional grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share receiving state or institutional grants by Pell Recipient Status

```{r chunk80418791} 
chartFn1(targetName="Total state and institutional grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Pell Recipient Status

```{r chunk66498923} 
chartFn1(targetName="Total state and institutional grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share receiving state or institutional grants by Parents' Highest Education Level

```{r chunk43990511} 
chartFn1(targetName="Total state and institutional grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Parents' Highest Education Level

```{r chunk87630790} 
chartFn1(targetName="Total state and institutional grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share receiving state or institutional grants by Race/Ethnicity

```{r chunk97731556} 
chartFn1(targetName="Total state and institutional grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Race/Ethnicity

```{r chunk9416067} 
chartFn1(targetName="Total state and institutional grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share receiving state or institutional grants by Institution HBCU Status

```{r chunk28009272} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Institution HBCU Status

```{r chunk39836673} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share receiving state or institutional grants by Institution MSI Status

```{r chunk56741783} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Institution MSI Status

```{r chunk3710642} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share receiving state or institutional grants by Institution Selectivity

```{r chunk56854978} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Institution Selectivity

```{r chunk53096604} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share receiving state or institutional grants by Institution State

```{r chunk66889175} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average combined state and institutional grant award by Institution State

```{r chunk37552824} 
chartFn1(targetName="Total state and institutional grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Grant amount exceeding federal need

####  {.tabset}

##### By Income Quartile

###### Share whose grants exceed federal need by Income Quartile

```{r chunk323187} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Income Quartile

```{r chunk52589831} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share whose grants exceed federal need by Zero EFC Status

```{r chunk30058040} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Zero EFC Status

```{r chunk98041459} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share whose grants exceed federal need by Pell Recipient Status

```{r chunk40577623} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Pell Recipient Status

```{r chunk39333777} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share whose grants exceed federal need by Parents' Highest Education Level

```{r chunk23680361} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Parents' Highest Education Level

```{r chunk41888744} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share whose grants exceed federal need by Race/Ethnicity

```{r chunk21740877} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Race/Ethnicity

```{r chunk2832997} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share whose grants exceed federal need by Institution HBCU Status

```{r chunk9570250} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Institution HBCU Status

```{r chunk28327742} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share whose grants exceed federal need by Institution MSI Status

```{r chunk99025330} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Institution MSI Status

```{r chunk75660055} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share whose grants exceed federal need by Institution Selectivity

```{r chunk78590006} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Institution Selectivity

```{r chunk83746527} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share whose grants exceed federal need by Institution State

```{r chunk81635797} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average grant amount in excess of federal need by Institution State

```{r chunk59717321} 
chartFn1(targetName="Grant amount exceeding federal need", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```

#### {-}

## Unit A4: Net price 

### Tuition and fees minus all grants

####  {.tabset}

##### By Income Quartile

###### Share with unmet tuition and fees after all grants by Income Quartile

```{r chunk30621285} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Income Quartile", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Income Quartile

```{r chunk88647911} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Income Quartile

```{r chunk38958751} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Share with unmet tuition and fees after all grants by Zero EFC Status

```{r chunk4310080} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Zero EFC Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Zero EFC Status

```{r chunk20597620} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Zero EFC Status

```{r chunk39586079} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Share with unmet tuition and fees after all grants by Pell Recipient Status

```{r chunk78130159} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Pell Recipient Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Pell Recipient Status

```{r chunk45865292} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Pell Recipient Status

```{r chunk69839582} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Share with unmet tuition and fees after all grants by Parents' Highest Education Level

```{r chunk8938016} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Parents' Highest Education Level

```{r chunk94571548} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Parents' Highest Education Level

```{r chunk78668323} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Share with unmet tuition and fees after all grants by Race/Ethnicity

```{r chunk29988756} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Race/Ethnicity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Race/Ethnicity

```{r chunk31577731} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Race/Ethnicity

```{r chunk47284659} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Share with unmet tuition and fees after all grants by Institution HBCU Status

```{r chunk77860182} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution HBCU Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Institution HBCU Status

```{r chunk22197055} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Institution HBCU Status

```{r chunk47676141} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Share with unmet tuition and fees after all grants by Institution MSI Status

```{r chunk39181036} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution MSI Status", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Institution MSI Status

```{r chunk71352407} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Institution MSI Status

```{r chunk9583780} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Share with unmet tuition and fees after all grants by Institution Selectivity

```{r chunk28240668} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution Selectivity", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Institution Selectivity

```{r chunk98356470} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Institution Selectivity

```{r chunk91089236} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Share with unmet tuition and fees after all grants by Institution State

```{r chunk71001855} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution State", measureName="Share >0", subtable="SECTOR3", sector3Val="None")
```
 
###### Average net tuition and fees after all grants by Institution State

```{r chunk9243579} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net tuition and fees after all grants by Institution State

```{r chunk62652923} 
chartFn1(targetName="Tuition and fees minus all grants", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Net tuition after all grants as percent of income

####  {.tabset}

##### By Income Quartile

###### Median net tuition and fees after all grants as a percentage of income by Income Quartile

```{r chunk51626285} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median net tuition and fees after all grants as a percentage of income by Zero EFC Status

```{r chunk67481360} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median net tuition and fees after all grants as a percentage of income by Pell Recipient Status

```{r chunk41637712} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median net tuition and fees after all grants as a percentage of income by Parents' Highest Education Level

```{r chunk16570251} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median net tuition and fees after all grants as a percentage of income by Race/Ethnicity

```{r chunk23036083} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median net tuition and fees after all grants as a percentage of income by Institution HBCU Status

```{r chunk47649822} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Median net tuition and fees after all grants as a percentage of income by Institution MSI Status

```{r chunk13580993} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Median net tuition and fees after all grants as a percentage of income by Institution Selectivity

```{r chunk74075400} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median net tuition and fees after all grants as a percentage of income by Institution State

```{r chunk26625888} 
chartFn1(targetName="Net tuition after all grants as percent of income", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Student budget minus all grants

####  {.tabset}

##### By Income Quartile

###### Average net student budget after all grants by Income Quartile

```{r chunk7072322} 
chartFn1(targetName="Student budget minus all grants", rowName="Income Quartile", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Income Quartile

```{r chunk30090899} 
chartFn1(targetName="Student budget minus all grants", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Average net student budget after all grants by Zero EFC Status

```{r chunk92374924} 
chartFn1(targetName="Student budget minus all grants", rowName="Zero EFC Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Zero EFC Status

```{r chunk5701617} 
chartFn1(targetName="Student budget minus all grants", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Average net student budget after all grants by Pell Recipient Status

```{r chunk81093029} 
chartFn1(targetName="Student budget minus all grants", rowName="Pell Recipient Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Pell Recipient Status

```{r chunk26365901} 
chartFn1(targetName="Student budget minus all grants", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Average net student budget after all grants by Parents' Highest Education Level

```{r chunk55900684} 
chartFn1(targetName="Student budget minus all grants", rowName="Parents' Highest Education Level", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Parents' Highest Education Level

```{r chunk2096444} 
chartFn1(targetName="Student budget minus all grants", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Average net student budget after all grants by Race/Ethnicity

```{r chunk12721994} 
chartFn1(targetName="Student budget minus all grants", rowName="Race/Ethnicity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Race/Ethnicity

```{r chunk73716230} 
chartFn1(targetName="Student budget minus all grants", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Average net student budget after all grants by Institution HBCU Status

```{r chunk6648436} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution HBCU Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Institution HBCU Status

```{r chunk24905843} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Average net student budget after all grants by Institution MSI Status

```{r chunk62139759} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution MSI Status", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Institution MSI Status

```{r chunk89582824} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Average net student budget after all grants by Institution Selectivity

```{r chunk66253929} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution Selectivity", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Institution Selectivity

```{r chunk17009305} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Average net student budget after all grants by Institution State

```{r chunk44753364} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution State", measureName="Average", subtable="SECTOR3", sector3Val="None")
```
 
###### Median net student budget after all grants by Institution State

```{r chunk23874514} 
chartFn1(targetName="Student budget minus all grants", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Net price after grants as percent of income

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants as a percentage of income by Income Quartile

```{r chunk72072136} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median net student budget after all grants as a percentage of income by Zero EFC Status

```{r chunk8964842} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median net student budget after all grants as a percentage of income by Pell Recipient Status

```{r chunk21497503} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median net student budget after all grants as a percentage of income by Parents' Highest Education Level

```{r chunk84612892} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median net student budget after all grants as a percentage of income by Race/Ethnicity

```{r chunk82607451} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median net student budget after all grants as a percentage of income by Institution HBCU Status

```{r chunk4582512} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Median net student budget after all grants as a percentage of income by Institution MSI Status

```{r chunk16005624} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Median net student budget after all grants as a percentage of income by Institution Selectivity

```{r chunk77476082} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median net student budget after all grants as a percentage of income by Institution State

```{r chunk66410707} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

## Unit A5: Context 

### Expected Family Contribution

####  {.tabset}

##### By Income Quartile

###### Median Expected Family Contribution by Income Quartile

```{r chunk26529325} 
chartFn1(targetName="Expected Family Contribution", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median Expected Family Contribution by Zero EFC Status

```{r chunk55034380} 
chartFn1(targetName="Expected Family Contribution", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median Expected Family Contribution by Pell Recipient Status

```{r chunk14627895} 
chartFn1(targetName="Expected Family Contribution", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median Expected Family Contribution by Parents' Highest Education Level

```{r chunk80785932} 
chartFn1(targetName="Expected Family Contribution", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median Expected Family Contribution by Race/Ethnicity

```{r chunk127443} 
chartFn1(targetName="Expected Family Contribution", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median Expected Family Contribution by Institution HBCU Status

```{r chunk40513851} 
chartFn1(targetName="Expected Family Contribution", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Median Expected Family Contribution by Institution MSI Status

```{r chunk53877674} 
chartFn1(targetName="Expected Family Contribution", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Median Expected Family Contribution by Institution Selectivity

```{r chunk18454728} 
chartFn1(targetName="Expected Family Contribution", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median Expected Family Contribution by Institution State

```{r chunk79815942} 
chartFn1(targetName="Expected Family Contribution", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Tuition and fees paid

####  {.tabset}

##### By Income Quartile

###### Median tuition and fees paid by Income Quartile

```{r chunk57895933} 
chartFn1(targetName="Tuition and fees paid", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median tuition and fees paid by Zero EFC Status

```{r chunk38153193} 
chartFn1(targetName="Tuition and fees paid", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median tuition and fees paid by Pell Recipient Status

```{r chunk70198910} 
chartFn1(targetName="Tuition and fees paid", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median tuition and fees paid by Parents' Highest Education Level

```{r chunk48566414} 
chartFn1(targetName="Tuition and fees paid", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median tuition and fees paid by Race/Ethnicity

```{r chunk53374166} 
chartFn1(targetName="Tuition and fees paid", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median tuition and fees paid by Institution HBCU Status

```{r chunk44091555} 
chartFn1(targetName="Tuition and fees paid", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median tuition and fees paid by Institution State

```{r chunk77302470} 
chartFn1(targetName="Tuition and fees paid", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

### Student budget (attendance adjusted)

####  {.tabset}

##### By Income Quartile

###### Median student budget (attendance adjusted) by Income Quartile

```{r chunk82433907} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Income Quartile", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Zero EFC Status

###### Median student budget (attendance adjusted) by Zero EFC Status

```{r chunk77385065} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Zero EFC Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Pell Recipient Status

###### Median student budget (attendance adjusted) by Pell Recipient Status

```{r chunk6279823} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Pell Recipient Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Parents' Highest Education Level

###### Median student budget (attendance adjusted) by Parents' Highest Education Level

```{r chunk45346010} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Parents' Highest Education Level", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Race/Ethnicity

###### Median student budget (attendance adjusted) by Race/Ethnicity

```{r chunk49422474} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Race/Ethnicity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution HBCU Status

###### Median student budget (attendance adjusted) by Institution HBCU Status

```{r chunk98537518} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Institution HBCU Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution MSI Status

###### Median student budget (attendance adjusted) by Institution MSI Status

```{r chunk70474364} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Institution MSI Status", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution Selectivity

###### Median student budget (attendance adjusted) by Institution Selectivity

```{r chunk71053720} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Institution Selectivity", measureName="Median", subtable="SECTOR3", sector3Val="None")
```
 
##### By Institution State

###### Median student budget (attendance adjusted) by Institution State

```{r chunk14462049} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Institution State", measureName="Median", subtable="SECTOR3", sector3Val="None")
```

#### {-}

# Section B: State public four-year sectors

## Unit B1: Distributions of aid programs

### State grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving State grants by Income Quartile

```{r chunk17568446} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Income Quartile

```{r chunk59735096} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Share receiving State grants by Zero EFC Status

```{r chunk89249568} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Zero EFC Status

```{r chunk64577192} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Share receiving State grants by Pell Recipient Status

```{r chunk80032095} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Pell Recipient Status

```{r chunk5125527} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Share receiving State grants by Parents' Highest Education Level

```{r chunk15023497} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Parents' Highest Education Level

```{r chunk96070968} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Share receiving State grants by Race/Ethnicity

```{r chunk16749953} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average State grant award by Race/Ethnicity

```{r chunk35949109} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

### Institution grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving Institution grants by Income Quartile

```{r chunk50745611} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Income Quartile

```{r chunk43216176} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Share receiving Institution grants by Zero EFC Status

```{r chunk3574275} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Zero EFC Status

```{r chunk43692847} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Share receiving Institution grants by Pell Recipient Status

```{r chunk37216563} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Pell Recipient Status

```{r chunk56041219} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Share receiving Institution grants by Parents' Highest Education Level

```{r chunk27815223} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Parents' Highest Education Level

```{r chunk36710235} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Share receiving Institution grants by Race/Ethnicity

```{r chunk8318392} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 4-year")
```

###### Average Institution grant award by Race/Ethnicity

```{r chunk93558017} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Average", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

## Unit B2: Net price

### Student budget minus all grants

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants by Income Quartile

```{r chunk67220919} 
chartFn1(targetName="Student budget minus all grants", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Median net student budget after all grants by Zero EFC Status

```{r chunk90933196} 
chartFn1(targetName="Student budget minus all grants", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Median net student budget after all grants by Pell Recipient Status

```{r chunk5142312} 
chartFn1(targetName="Student budget minus all grants", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Median net student budget after all grants by Parents' Highest Education Level

```{r chunk57309913} 
chartFn1(targetName="Student budget minus all grants", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Median net student budget after all grants by Race/Ethnicity

```{r chunk95999672} 
chartFn1(targetName="Student budget minus all grants", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

### Net price after grants as percent of income

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants as a percentage of income by Income Quartile

```{r chunk77671417} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Median net student budget after all grants as a percentage of income by Zero EFC Status

```{r chunk40101387} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Median net student budget after all grants as a percentage of income by Pell Recipient Status

```{r chunk24887600} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Median net student budget after all grants as a percentage of income by Parents' Highest Education Level

```{r chunk9663917} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Median net student budget after all grants as a percentage of income by Race/Ethnicity

```{r chunk61505285} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

## Unit B3: Context

### Student budget (attendance adjusted)

####  {.tabset}

##### By Income Quartile

###### Median student budget (attendance adjusted) by Income Quartile

```{r chunk24593966} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Zero EFC Status

###### Median student budget (attendance adjusted) by Zero EFC Status

```{r chunk35111846} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Pell Recipient Status

###### Median student budget (attendance adjusted) by Pell Recipient Status

```{r chunk98776166} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Parents' Highest Education Level

###### Median student budget (attendance adjusted) by Parents' Highest Education Level

```{r chunk6461224} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

##### By Race/Ethnicity

###### Median student budget (attendance adjusted) by Race/Ethnicity

```{r chunk56663130} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 4-year")
```

#### {-}

# Section C: State public two-year sectors

## Unit C1: Distributions of aid programs

### State grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving State grants by Income Quartile

```{r chunk49571211} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Income Quartile

```{r chunk46240588} 
chartFn1(targetName="State grants total", rowName="Income Quartile", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Share receiving State grants by Zero EFC Status

```{r chunk52618371} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Zero EFC Status

```{r chunk52566867} 
chartFn1(targetName="State grants total", rowName="Zero EFC Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Share receiving State grants by Pell Recipient Status

```{r chunk29946108} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Pell Recipient Status

```{r chunk51567092} 
chartFn1(targetName="State grants total", rowName="Pell Recipient Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Share receiving State grants by Parents' Highest Education Level

```{r chunk72062326} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Parents' Highest Education Level

```{r chunk40281} 
chartFn1(targetName="State grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Share receiving State grants by Race/Ethnicity

```{r chunk20996483} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average State grant award by Race/Ethnicity

```{r chunk72835120} 
chartFn1(targetName="State grants total", rowName="Race/Ethnicity", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

### Institution grants total

####  {.tabset}

##### By Income Quartile

###### Share receiving Institution grants by Income Quartile

```{r chunk90179463} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Income Quartile

```{r chunk31221467} 
chartFn1(targetName="Institution grants total", rowName="Income Quartile", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Share receiving Institution grants by Zero EFC Status

```{r chunk49250283} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Zero EFC Status

```{r chunk13852389} 
chartFn1(targetName="Institution grants total", rowName="Zero EFC Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Share receiving Institution grants by Pell Recipient Status

```{r chunk10271378} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Pell Recipient Status

```{r chunk13125137} 
chartFn1(targetName="Institution grants total", rowName="Pell Recipient Status", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Share receiving Institution grants by Parents' Highest Education Level

```{r chunk38214239} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Parents' Highest Education Level

```{r chunk75445375} 
chartFn1(targetName="Institution grants total", rowName="Parents' Highest Education Level", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Share receiving Institution grants by Race/Ethnicity

```{r chunk59264608} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Share >0", subtable="INSTSTAT", sector3Val="Public 2-year")
```

###### Average Institution grant award by Race/Ethnicity

```{r chunk35185685} 
chartFn1(targetName="Institution grants total", rowName="Race/Ethnicity", measureName="Average", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

## Unit C2: Net price

### Student budget minus all grants

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants by Income Quartile

```{r chunk18536958} 
chartFn1(targetName="Student budget minus all grants", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Median net student budget after all grants by Zero EFC Status

```{r chunk47333721} 
chartFn1(targetName="Student budget minus all grants", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Median net student budget after all grants by Pell Recipient Status

```{r chunk67817845} 
chartFn1(targetName="Student budget minus all grants", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Median net student budget after all grants by Parents' Highest Education Level

```{r chunk17492098} 
chartFn1(targetName="Student budget minus all grants", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Median net student budget after all grants by Race/Ethnicity

```{r chunk68366166} 
chartFn1(targetName="Student budget minus all grants", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

### Net price after grants as percent of income

####  {.tabset}

##### By Income Quartile

###### Median net student budget after all grants as a percentage of income by Income Quartile

```{r chunk31999616} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Median net student budget after all grants as a percentage of income by Zero EFC Status

```{r chunk84794674} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Median net student budget after all grants as a percentage of income by Pell Recipient Status

```{r chunk49717969} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Median net student budget after all grants as a percentage of income by Parents' Highest Education Level

```{r chunk65967164} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Median net student budget after all grants as a percentage of income by Race/Ethnicity

```{r chunk80743284} 
chartFn1(targetName="Net price after grants as percent of income", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

## Unit C3: Context

####  {.tabset}

### Student budget (attendance adjusted)

##### By Income Quartile

###### Median student budget (attendance adjusted) by Income Quartile

```{r chunk79634960} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Income Quartile", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Zero EFC Status

###### Median student budget (attendance adjusted) by Zero EFC Status

```{r chunk28112054} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Zero EFC Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Pell Recipient Status

###### Median student budget (attendance adjusted) by Pell Recipient Status

```{r chunk47516273} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Pell Recipient Status", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Parents' Highest Education Level

###### Median student budget (attendance adjusted) by Parents' Highest Education Level

```{r chunk85050934} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Parents' Highest Education Level", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

##### By Race/Ethnicity

###### Median student budget (attendance adjusted) by Race/Ethnicity

```{r chunk47244698} 
chartFn1(targetName="Student budget (attendance adjusted)", rowName="Race/Ethnicity", measureName="Median", subtable="INSTSTAT", sector3Val="Public 2-year")
```

#### {-}

# Section D: Distributions across variables 

## Unit D1: Distributions across variables 

### Income Quartile

####  {.tabset}

##### Overall

###### Distribution of Income Quartile

```{r chunk21285487} 
chartFn2(distributionName="Income Quartile", rowName="Overall")
```
 
##### By Zero EFC Status

###### Distribution of Income Quartile by Zero EFC Status

```{r chunk61110952} 
chartFn2(distributionName="Income Quartile", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Income Quartile by Pell Recipient Status

```{r chunk60880357} 
chartFn2(distributionName="Income Quartile", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Income Quartile by Parents' Highest Education Level

```{r chunk50159729} 
chartFn2(distributionName="Income Quartile", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Income Quartile by Race/Ethnicity

```{r chunk2673506} 
chartFn2(distributionName="Income Quartile", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Income Quartile by Institution HBCU Status

```{r chunk81535522} 
chartFn2(distributionName="Income Quartile", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Income Quartile by Institution MSI Status

```{r chunk97252930} 
chartFn2(distributionName="Income Quartile", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Income Quartile by Institution Selectivity

```{r chunk88980865} 
chartFn2(distributionName="Income Quartile", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Income Quartile by Institution State

```{r chunk76352259} 
chartFn2(distributionName="Income Quartile", rowName="Institution State")
```

#### {-}

### Zero EFC Status

####  {.tabset}

##### Overall

###### Distribution of Zero EFC Status

```{r chunk52557812} 
chartFn2(distributionName="Zero EFC Status", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Zero EFC Status by Income Quartile

```{r chunk62877694} 
chartFn2(distributionName="Zero EFC Status", rowName="Income Quartile")
```
 
##### By Pell Recipient Status

###### Distribution of Zero EFC Status by Pell Recipient Status

```{r chunk22397449} 
chartFn2(distributionName="Zero EFC Status", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Zero EFC Status by Parents' Highest Education Level

```{r chunk1739577} 
chartFn2(distributionName="Zero EFC Status", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Zero EFC Status by Race/Ethnicity

```{r chunk93806167} 
chartFn2(distributionName="Zero EFC Status", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Zero EFC Status by Institution HBCU Status

```{r chunk60057384} 
chartFn2(distributionName="Zero EFC Status", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Zero EFC Status by Institution MSI Status

```{r chunk13462969} 
chartFn2(distributionName="Zero EFC Status", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Zero EFC Status by Institution Selectivity

```{r chunk21818645} 
chartFn2(distributionName="Zero EFC Status", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Zero EFC Status by Institution State

```{r chunk66404237} 
chartFn2(distributionName="Zero EFC Status", rowName="Institution State")
```

#### {-}

### Pell Recipient Status

####  {.tabset}

##### Overall

###### Distribution of Pell Recipient Status

```{r chunk50423723} 
chartFn2(distributionName="Pell Recipient Status", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Pell Recipient Status by Income Quartile

```{r chunk10341132} 
chartFn2(distributionName="Pell Recipient Status", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Pell Recipient Status by Zero EFC Status

```{r chunk87337223} 
chartFn2(distributionName="Pell Recipient Status", rowName="Zero EFC Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Pell Recipient Status by Parents' Highest Education Level

```{r chunk20513581} 
chartFn2(distributionName="Pell Recipient Status", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Pell Recipient Status by Race/Ethnicity

```{r chunk21042589} 
chartFn2(distributionName="Pell Recipient Status", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Pell Recipient Status by Institution HBCU Status

```{r chunk8637916} 
chartFn2(distributionName="Pell Recipient Status", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Pell Recipient Status by Institution MSI Status

```{r chunk34446016} 
chartFn2(distributionName="Pell Recipient Status", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Pell Recipient Status by Institution Selectivity

```{r chunk93142296} 
chartFn2(distributionName="Pell Recipient Status", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Pell Recipient Status by Institution State

```{r chunk53915545} 
chartFn2(distributionName="Pell Recipient Status", rowName="Institution State")
```

#### {-}

### Parents' Highest Education Level

####  {.tabset}

##### Overall

###### Distribution of Parents' Highest Education Level

```{r chunk50981952} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Parents' Highest Education Level by Income Quartile

```{r chunk10634790} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Parents' Highest Education Level by Zero EFC Status

```{r chunk7337061} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Parents' Highest Education Level by Pell Recipient Status

```{r chunk83980521} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Pell Recipient Status")
```
 
##### By Race/Ethnicity

###### Distribution of Parents' Highest Education Level by Race/Ethnicity

```{r chunk20888415} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Parents' Highest Education Level by Institution HBCU Status

```{r chunk11742342} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Parents' Highest Education Level by Institution MSI Status

```{r chunk449097} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Parents' Highest Education Level by Institution Selectivity

```{r chunk55869199} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Parents' Highest Education Level by Institution State

```{r chunk40402759} 
chartFn2(distributionName="Parents' Highest Education Level", rowName="Institution State")
```

#### {-}

### Race/Ethnicity

####  {.tabset}

##### Overall

###### Distribution of Race/Ethnicity

```{r chunk83424412} 
chartFn2(distributionName="Race/Ethnicity", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Race/Ethnicity by Income Quartile

```{r chunk97835230} 
chartFn2(distributionName="Race/Ethnicity", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Race/Ethnicity by Zero EFC Status

```{r chunk43878198} 
chartFn2(distributionName="Race/Ethnicity", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Race/Ethnicity by Pell Recipient Status

```{r chunk62457188} 
chartFn2(distributionName="Race/Ethnicity", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Race/Ethnicity by Parents' Highest Education Level

```{r chunk37090882} 
chartFn2(distributionName="Race/Ethnicity", rowName="Parents' Highest Education Level")
```
 
##### By Institution HBCU Status

###### Distribution of Race/Ethnicity by Institution HBCU Status

```{r chunk5361692} 
chartFn2(distributionName="Race/Ethnicity", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Race/Ethnicity by Institution MSI Status

```{r chunk78950206} 
chartFn2(distributionName="Race/Ethnicity", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Race/Ethnicity by Institution Selectivity

```{r chunk36318482} 
chartFn2(distributionName="Race/Ethnicity", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Race/Ethnicity by Institution State

```{r chunk5826190} 
chartFn2(distributionName="Race/Ethnicity", rowName="Institution State")
```

#### {-}

### High School GPA

####  {.tabset}

##### By Income Quartile

###### Distribution of High School GPA by Income Quartile

```{r chunk69111367} 
chartFn2(distributionName="High School GPA", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of High School GPA by Zero EFC Status

```{r chunk78838351} 
chartFn2(distributionName="High School GPA", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of High School GPA by Pell Recipient Status

```{r chunk4480418} 
chartFn2(distributionName="High School GPA", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of High School GPA by Parents' Highest Education Level

```{r chunk15614645} 
chartFn2(distributionName="High School GPA", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of High School GPA by Race/Ethnicity

```{r chunk23645188} 
chartFn2(distributionName="High School GPA", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of High School GPA by Institution HBCU Status

```{r chunk21585575} 
chartFn2(distributionName="High School GPA", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of High School GPA by Institution MSI Status

```{r chunk88406244} 
chartFn2(distributionName="High School GPA", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of High School GPA by Institution Selectivity

```{r chunk61918527} 
chartFn2(distributionName="High School GPA", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of High School GPA by Institution State

```{r chunk58769353} 
chartFn2(distributionName="High School GPA", rowName="Institution State")
```

#### {-}

### Institution HBCU Status

####  {.tabset}

##### Overall

###### Distribution of Institution HBCU Status

```{r chunk56654027} 
chartFn2(distributionName="Institution HBCU Status", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Institution HBCU Status by Income Quartile

```{r chunk62720479} 
chartFn2(distributionName="Institution HBCU Status", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Institution HBCU Status by Zero EFC Status

```{r chunk76775898} 
chartFn2(distributionName="Institution HBCU Status", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Institution HBCU Status by Pell Recipient Status

```{r chunk34456158} 
chartFn2(distributionName="Institution HBCU Status", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Institution HBCU Status by Parents' Highest Education Level

```{r chunk4705165} 
chartFn2(distributionName="Institution HBCU Status", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Institution HBCU Status by Race/Ethnicity

```{r chunk81936383} 
chartFn2(distributionName="Institution HBCU Status", rowName="Race/Ethnicity")
```
 
##### By Institution MSI Status

###### Distribution of Institution HBCU Status by Institution MSI Status

```{r chunk96629739} 
chartFn2(distributionName="Institution HBCU Status", rowName="Institution MSI Status")
```
 
##### By Institution Selectivity

###### Distribution of Institution HBCU Status by Institution Selectivity

```{r chunk57559333} 
chartFn2(distributionName="Institution HBCU Status", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Institution HBCU Status by Institution State

```{r chunk2439493} 
chartFn2(distributionName="Institution HBCU Status", rowName="Institution State")
```

#### {-}

### Institution MSI Status

####  {.tabset}

##### Overall

###### Distribution of Institution MSI Status

```{r chunk41735544} 
chartFn2(distributionName="Institution MSI Status", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Institution MSI Status by Income Quartile

```{r chunk24690406} 
chartFn2(distributionName="Institution MSI Status", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Institution MSI Status by Zero EFC Status

```{r chunk36081062} 
chartFn2(distributionName="Institution MSI Status", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Institution MSI Status by Pell Recipient Status

```{r chunk90438112} 
chartFn2(distributionName="Institution MSI Status", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Institution MSI Status by Parents' Highest Education Level

```{r chunk62713825} 
chartFn2(distributionName="Institution MSI Status", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Institution MSI Status by Race/Ethnicity

```{r chunk57783129} 
chartFn2(distributionName="Institution MSI Status", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Institution MSI Status by Institution HBCU Status

```{r chunk20928641} 
chartFn2(distributionName="Institution MSI Status", rowName="Institution HBCU Status")
```
 
##### By Institution Selectivity

###### Distribution of Institution MSI Status by Institution Selectivity

```{r chunk37268494} 
chartFn2(distributionName="Institution MSI Status", rowName="Institution Selectivity")
```
 
##### By Institution State

###### Distribution of Institution MSI Status by Institution State

```{r chunk35218199} 
chartFn2(distributionName="Institution MSI Status", rowName="Institution State")
```

#### {-}

### Institution Selectivity

####  {.tabset}

##### Overall

###### Distribution of Institution Selectivity

```{r chunk86891062} 
chartFn2(distributionName="Institution Selectivity", rowName="Overall")
```
 
##### By Income Quartile

###### Distribution of Institution Selectivity by Income Quartile

```{r chunk24159689} 
chartFn2(distributionName="Institution Selectivity", rowName="Income Quartile")
```
 
##### By Zero EFC Status

###### Distribution of Institution Selectivity by Zero EFC Status

```{r chunk71251531} 
chartFn2(distributionName="Institution Selectivity", rowName="Zero EFC Status")
```
 
##### By Pell Recipient Status

###### Distribution of Institution Selectivity by Pell Recipient Status

```{r chunk76016375} 
chartFn2(distributionName="Institution Selectivity", rowName="Pell Recipient Status")
```
 
##### By Parents' Highest Education Level

###### Distribution of Institution Selectivity by Parents' Highest Education Level

```{r chunk21428687} 
chartFn2(distributionName="Institution Selectivity", rowName="Parents' Highest Education Level")
```
 
##### By Race/Ethnicity

###### Distribution of Institution Selectivity by Race/Ethnicity

```{r chunk51678473} 
chartFn2(distributionName="Institution Selectivity", rowName="Race/Ethnicity")
```
 
##### By Institution HBCU Status

###### Distribution of Institution Selectivity by Institution HBCU Status

```{r chunk41283899} 
chartFn2(distributionName="Institution Selectivity", rowName="Institution HBCU Status")
```
 
##### By Institution MSI Status

###### Distribution of Institution Selectivity by Institution MSI Status

```{r chunk65594084} 
chartFn2(distributionName="Institution Selectivity", rowName="Institution MSI Status")
```
 
##### By Institution State

###### Distribution of Institution Selectivity by Institution State

```{r chunk60829118} 
chartFn2(distributionName="Institution Selectivity", rowName="Institution State")
```

#### {-}


